### 2018-06-27 paper/Manuscript.tex

%File Generated with PyPaper
\documentclass[aps,prl,reprint,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress,twocolumn]{revtex4-1}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{stackengine}
\usepackage[dvipsnames*,svgnames]{xcolor}
\usepackage{verbatim}
\usepackage[position=bottom,caption=false,captionskip=3pt,font=normalsize,subrefformat=simple,labelformat=simple]{subfig}
\renewcommand{\thesubfigure}{(\alph{subfigure})}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{chngcntr}
\usepackage{bm}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\newcommand {\framedgraphic}[2] {\begin{frame}{#1}\begin{center}\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{#2}\end{center}\end{frame}}\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}
\usepackage{tabularx}
\usepackage{soul}
\hypersetup{
colorlinks,
linkcolor={blue!100!black},
citecolor={blue},
urlcolor={blue!80!black}}
\lstset{basicstyle=\small\ttfamily,columns=flexible,breaklines=true}\newcommand{\fakesection}[1]{\par\refstepcounter{section}\sectionmark{#1}\addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}}\def\equationautorefname~#1\null{#1\null}
\raggedbottom\usepackage[bottom]{footmisc} \makeatletter \def\p@section{} \def\p@subsubsection{} \makeatother\begin{document}
\title{Byesim: a tool for fast device characterization with Bayesian inference}
\author{Rachel Kurchin}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\author{Giuseppe Romano}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\author{Tonio Buonassisi}
\email{buonassi@mit.edu}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\begin{abstract}
Achieving low thermal conductivity and good electrical properties is a crucial condition for thermal energy harvesting materials. Nanostructuring offers a very powerful tool to address both requirements: in nanostructured materials, boundaries preferentially scatter phonons compared to electrons. The search for low-thermal conductivity nanostructures is typically limited to materials with simple crystal structures, such as silicon, because of the complexity arising from modeling branch- and wave vector-dependent nanoscale heat transport. Using the phonon mean-free-path (MFP) dependent Boltzmann transport equation, a model that overcomes this limitation, we compute thermal transport in 75 nanoporous Half Heusler compounds for different pore sizes. We demonstrate that the optimization of thermal transport in nanostructures should take into account both bulk thermal properties and geometry-dependent phonon suppression, two aspects that are typically engineered separately. In fact, our work predicts that, given a set of bulk materials and a system geometry, the ordering of the bulk thermal conductivity does not necessarily align with that of the nanostructure. We show that what dictates thermal transport is the interplay between the bulk MFP distribution and the material's characteristic length. Finally, we derive a thermal transport model than enables fast systems screening within large bulk material repositories and a given geometry. Our study motivates the need for a holistic approach in engineering thermal transport and provides a method for high-throughput materials discovery.\end{abstract}
\maketitle

\section*{Acknowledgements}
Research supported as part of the Solid-State Solar-Thermal Energy Conversion Center (S3TEC), an Energy Frontier Research Center funded by the US Department of Energy (DOE), Office of Science, Basic Energy Sciences (BES), under Award DESC0001.\par 
\begin{equation}
\begin{split}\label{Eq:1001}
E=mc^2 
\end{split}
\end{equation}

\section*{Introduction}
Example of referencens as seen in ~\cite{fugallo2014thermal} and this refers to fig ~\subref*{Fig:10a}referes the Eq. ~(\autoref{Eq:1001}) 
\begin{figure*}[!ht]

\subfloat[\label{Fig:10a}]
{\includegraphics[width=0.48\textwidth]{./figure_1a.png}}
\hfill
\subfloat[\label{Fig:10b}]
{\includegraphics[width=0.48\textwidth]{./figure_1b.png}}
\caption{}
\end{figure*}
 %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{1}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Fugallo}\ \emph {et~al.}(2014)\citenamefont
  {Fugallo}, \citenamefont {Cepellotti}, \citenamefont {Paulatto},
  \citenamefont {Lazzeri}, \citenamefont {Marzari},\ and\ \citenamefont
  {Mauri}}]{fugallo2014thermal}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Fugallo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Cepellotti}},
  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Paulatto}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Lazzeri}}, \bibinfo {author}
  {\bibfnamefont {N.}~\bibnamefont {Marzari}}, \ and\ \bibinfo {author}
  {\bibfnamefont {F.}~\bibnamefont {Mauri}},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Nano letters}\ }\textbf {\bibinfo {volume}
  {14}},\ \bibinfo {pages} {6109} (\bibinfo {year} {2014})}\BibitemShut
  {NoStop}%
\end{thebibliography}%
\end{document}

### 2018-06-27 bayesim/model.py
barebones version of accepting file inputs works

@@ -52,21 +52,21 @@ class model(object):
         self.probs = pmf.Pmf(self.fit_params)
 
 
-    def attach_observations(self,argv):
+    def attach_observations(self,**argv):
         """
         Attach measured dataset.
         """
         mode = argv.setdefault('mode','file')
 
         if mode == 'file':
-          self.obs_data = dd.io.load(argv['fpath'])['data']
+          self.obs_data = dd.io.load(argv['fpath'])
         else:
           self.obs_data = eval(argv['name']+'()')
 
 
-    def attach_model(self,argv):
+    def attach_model(self,**argv):
         """
-        Attach the model for the data, either by feeding in a file of precomputed data or a function that does the computing.argv
+        Attach the model for the data, either by feeding in a file of precomputed data or a function that does the computing.
 
         Args:
             mode (`str`): either 'file' or 'function' - should only use the latter if using an analytical model
@@ -75,6 +75,7 @@ class model(object):
 
         Todo:
             Figure out best way to check for correct formatting in an input file
+            Will this function also be used to attach new simulated data or should that be separate?
         """
 
         mode = argv.setdefault('mode','file')

### 2018-06-27 bayesim/model.py
I think everything we need for argparse is working :)

@@ -1,4 +1,4 @@
-import bayesim.pmf as pmf
+from bayesim.pmf import Pmf
 import pandas as pd
 import deepdish as dd
 from copy import deepcopy
@@ -19,6 +19,7 @@ class model(object):
         fix inputs to different functions (messy)
         make sure everything can accept files as inputs (important for argparse)
         add save_state function that writes hdf5 with all current variables
+        maybe make entire state into a dict?
 
     Todo:
         animating visualization during run
@@ -29,7 +30,7 @@ class model(object):
         put some of the pmf functions here to call directly (visualize, subdivide, etc.)
     """
 
-    def __init__(self,params,ec,output_var):
+    def __init__(self,**argv):
         """
         Initialize with a uniform PMF over the fitting parameters.
 
@@ -37,31 +38,56 @@ class model(object):
             fit_params (:obj:`param_list`): param_list object containing parameters to be fit and associated metadata
             ec (:obj:`list` of :obj:`str`): names of experimental conditions
             output_var (`str`): name of experimental output measurements
+            state_file (`str`): path to file saved by save_state() fcn - if this is provided, any other inputs will be ignored
         """
-        # should we do sanity checks here or at runtime?
-        # (i.e. checking that model_func doesn't require any inputs other than
-        # EC's or params already enumerated)
-        #self.fit_params = argv['fit_params']
-        self.fit_params = params.fit_params
-        #self.model_func = argv['model']
-        #self.ec = argv['ec']
-        self.ec = ec
-        self.output_var = output_var
 
-        # construct initial (uniform) probability distribution
-        self.probs = pmf.Pmf(self.fit_params)
+        if 'state_file' in argv.keys():
+            state = dd.io.load(argv['state_file'])
+            self.fit_params = state['fit_params']
+            self.ec = state['ec']
+            self.output_var = state['output_var']
+
+            self.probs = Pmf(self.fit_params)
+            self.probs.points = state['probs_points']
+
+            self.model_data = state['model_data']
+            self.needs_new_model_data = state['needs_new_model_data']
+            self.obs_data = state['obs_data']
+
+            self.start_indices = state['start_indices']
+            self.end_indices = state['end_indices']
+
+        else:
+            # read in inputs
+            self.fit_params = argv['params'].fit_params
+            self.ec = argv['ec']
+            self.output_var = argv['output_var']
+
+            # construct initial (uniform) probability distribution
+            self.probs = Pmf(self.fit_params)
+
+            # placeholders
[…]

### 2018-06-27 bayesim/pmf.py

@@ -13,6 +13,9 @@ class Pmf(object):
     Class that stores a PMF capable of nested sampling / "adaptive mesh refinement".
 
     Stores probabilities in a DataFrame which associates regions of parameter space with probability values.
+
+    Todo:
+        make a save_state function for this
     """
 
     def make_points_list(self, params, total_prob=1.0):

### 2018-06-27 bayesim/pmf.py
most of the new stuff added, none of it tested

@@ -66,7 +66,7 @@ class Pmf(object):
 
         # for now just copy in the param_list wholesale
         # eventually should probably scrub and/or update vals...
-        self.params = params
+        self.params = params.fit_params # last dot might be wrong
         self.points = self.make_points_list(self.params)
 
     def normalize(self):

### 2018-06-28 setup.py
argparse

@@ -10,7 +10,9 @@ setup(name='bayesim',
       classifiers=['Programming Language :: Python :: 2.7',\
                    'Programming Language :: Python :: 3.6'],
       long_description=open('README.rst').read(),
-      install_requires=['numpy', 
+      install_requires=['pandas',
+                        'deepdish',
+                        'numpy', 
                         'scipy',
                         'matplotlib',         
                          ],

### 2018-06-28 bayesim/model.py
committing before meeting

@@ -1,4 +1,5 @@
 from bayesim.pmf import Pmf
+import bayesim.param_list as pl
 import pandas as pd
 import deepdish as dd
 from copy import deepcopy
@@ -38,6 +39,7 @@ class model(object):
         Args:
             fit_params (:obj:`param_list`): param_list object containing parameters to be fit and associated metadata
             ec (:obj:`list` of :obj:`str`): names of experimental conditions
+            ec_tol_digits(`int`): number of digits to round off values of EC's (default 5)
             output_var (`str`): name of experimental output measurements
             load_state (`bool`): flag for whether to load state from a file - if True, other inputs (apart from state_file) are ignored
             state_file (`str`): path to file saved by save_state() fcn
@@ -47,6 +49,7 @@ class model(object):
         """
 
         state_file = argv.setdefault('state_file','bayesim_state.h5')
+        ec_tol_digits = argv.setdefault('ec_tol_digits',5)
 
         if argv['load_state']:
             state = dd.io.load(argv['state_file'])
@@ -56,6 +59,7 @@ class model(object):
             self.param_names = [p['name'] for p in self.fit_params]
             self.ec = state['ec']
             self.output_var = state['output_var']
+            self.ec_tol_digits = state['ec_tol_digits']
 
             # probabilities
             self.probs = Pmf(self.fit_params)
@@ -72,6 +76,7 @@ class model(object):
         else:
             # read in inputs
             self.output_var = argv['output_var']
+            self.ec_tol_digits = ec_tol_digits
 
             if 'params' in argv.keys():
                 self.probs = []
@@ -136,7 +141,7 @@ class model(object):
         if mode == 'file':
             self.obs_data = dd.io.load(argv['fpath'])
             # get EC names if necessary
-            cols = self.obs_data.columns
+            cols = list(self.obs_data.columns)
             if output_col not in cols:
                 raise NameError('Your output variable name, %s, is not the name of a column in your input data!', %(output_col))
                 break
@@ -167,27 +172,91 @@ class model(object):
             mode (`str`): either 'file' or 'function' - should only use the latter if using an analytical model
             func_name (callable): if mode='function', provide function here
             fpath (`str`): if mode='file', provide path to file
-
+            output_column (`str`): optional, header of column containing output data (required if different from self.output_var)
         Todo:
             Figure out best way to check for correct formatting in an input file
             Will this function also be used to attach new simulated data or should that be separate?
         """
 
[…]

### 2018-06-28 bayesim/param_list.py

@@ -16,26 +16,56 @@ class param_list(object):
 
         Args:
             name (str): name of parameter (required)
-            val_range (:obj:`list` of :obj:`float`): [min, max] (required)
+            val_range (:obj:`list` of :obj:`float`): [min, max] (either this or vals is required)
+            vals (:obj:`list` of :obj:`float`): full list of vals for this param
             length (int): initial length of this parameter (defaults to 10)
-            min_width(`float`): minimum box width for this parameter - subtractive if linear spacing and divisive if logarithmic (defaults to 0.01 of total range)
+            min_width(`float`): minimum box width for this parameter - subtractive if linear spacing and divisive if logarithmic (defaults to 0.01 of total range, required if providing val_range)
             spacing (str): 'linear' or 'log' (defaults to linear)
             units (str): units for this parameter, if any (defaults to 'unitless')
         """
-        # sanity checks
-        assert 'name' in argv and 'val_range' in argv, "Parameter must at least have a name and a range!"
-        val_range = argv['val_range']
-        assert len(val_range)==2 and val_range[1]>val_range[0], "val_range must be of length 2 with second entry larger than first!"
-
         # set some defaults - linear spacing, ten subdivisions, no units
         spacing = argv.setdefault('spacing','linear')
         length = argv.setdefault('length',10)
         units = argv.setdefault('units','unitless')
 
+        # sanity check
+        assert 'name' in argv and ('val_range' in argv or 'vals' in argv), "Parameter must at least have a name and a range!"
+
         # read in info
         param_info = dict(argv)
         spacing = param_info['spacing']
         length = param_info['length']
+
+        # compute edges and values
+        if 'val_range' in argv:
+            val_range = argv['val_range']
+            assert len(val_range)==2 and val_range[1]>val_range[0], "val_range must be of length 2 with second entry larger than first!"
+            if spacing == 'linear':
+                edges_vals = np.linspace(val_range[0],val_range[1],2*length+1)
+            elif spacing == 'log':
+                edges_vals = np.logspace(np.log10(val_range[0]),np.log10(val_range[1]),2*length+1)
+            edges = edges_vals[::2]
+            vals = edges_vals[1:-1:2]
+        elif 'vals' in argv:
+            vals = argv['vals']
+            assert(len(vals)>=2), "vals should have at least two values"
[…]

### 2018-06-28 bayesim/pmf.py

@@ -16,6 +16,7 @@ class Pmf(object):
 
     Todo:
         make a save_state function for this
+        (long-term) allow for non-gridded parameter space (Voronoi? Or MCMC with no subdivision)
     """
 
     def make_points_list(self, params, total_prob=1.0):
@@ -58,16 +59,22 @@ class Pmf(object):
         return df
 
 
-    def __init__(self, params):
+    def __init__(self, **argv):
         """
+        Provide one argument or the other.
+
         Args:
             params (:obj:`param_list`): param_list object containing parameters to be fit and associated metadata
+            param_points (`DataFrame`): DataFrame containing all parameter points to start with
         """
 
-        # for now just copy in the param_list wholesale
-        # eventually should probably scrub and/or update vals...
-        self.params = params.fit_params # last dot might be wrong
-        self.points = self.make_points_list(self.params)
+        if 'params' in argv.keys():
+            # for now just copy in the param_list wholesale
+            # eventually should probably scrub and/or update vals...
+            self.params = params.fit_params # last dot might be wrong
+            self.points = self.make_points_list(self.params)
+        elif 'param_points' in argv.keys():
+
 
     def normalize(self):
         """Normalize overall PMF."""

### 2018-06-28 paper/manuscript.py
paper outline update

@@ -32,19 +32,20 @@ p.add_alias(r'''\mathbf{\hat{s}}''','s')
 
 p.set_title('Byesim: a tool for fast device characterization with Bayesian inference')
 
-p.add_abstract_sentence(r'''Achieving low thermal conductivity and good electrical properties is a crucial condition for thermal energy harvesting materials. Nanostructuring offers a very powerful tool to address both requirements: in nanostructured materials, boundaries preferentially scatter phonons compared to electrons. The search for low-thermal conductivity nanostructures is typically limited to materials with simple crystal structures, such as silicon, because of the complexity arising from modeling branch- and wave vector-dependent nanoscale heat transport. Using the phonon mean-free-path (MFP) dependent Boltzmann transport equation, a model that overcomes this limitation, we compute thermal transport in 75 nanoporous Half Heusler compounds for different pore sizes. We demonstrate that the optimization of thermal transport in nanostructures should take into account both bulk thermal properties and geometry-dependent phonon suppression, two aspects that are typically engineered separately. In fact, our work predicts that, given a set of bulk materials and a system geometry, the ordering of the bulk thermal conductivity does not necessarily align with that of the nanostructure. We show that what dictates thermal transport is the interplay between the bulk MFP distribution and the material's characteristic length. Finally, we derive a thermal transport model than enables fast systems screening within large bulk material repositories and a given geometry. Our study motivates the need for a holistic approach in engineering thermal transport and provides a method for high-throughput materials discovery.''')
[…]

### 2018-06-28 paper/manuscript.py
paper outline

@@ -55,11 +55,14 @@ con = p.get_new_section_id('Example with real data')
 
 
 con = p.get_new_section_id('Discussion')
+p.s('discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion ')
+
 con = p.get_new_section_id('Conslusions')
+p.s('conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions ')
 
 
 con = p.get_new_section_id('Acknowledgements')
-p.s(r'''Research supported as part of the Solid-State Solar-Thermal Energy Conversion Center (S3TEC), an Energy Frontier Research Center funded by the US Department of Energy (DOE), Office of Science, Basic Energy Sciences (BES), under Award DESC0001.''')
+p.s(r'''acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements ''')
 
 
 p.tex()

### 2018-06-28 paper/manuscript.py
paper outline

@@ -48,7 +48,7 @@ con = p.get_new_section_id('Model')
 p.s('Figure 1: flowchart')
 
 con = p.get_new_section_id('Software Architecture')
-
+p.s('Figure 2: structure of code')
 
 con = p.get_new_section_id('Example with diode')
 con = p.get_new_section_id('Example with real data')

### 2018-06-28 paper/manuscript.py
paper outline

@@ -36,7 +36,7 @@ p.add_abstract_sentence(r'''abstract abstract abstract abstract abstract abstrac
 
 con = p.get_new_section_id('Introduction')
 
-p.s('introduction')
+p.s('introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction ')
 #p.s('Example of referencens as seen in ' + p.cite('fugallo2014thermal') + r''' and this refers to fig ''' + p.ref(fig_1 + 'a') + r'''referes the Eq. ''' + p.ref(nn1),br=1)
 
 #p.add_equation(r'''E=mc^2 ''',label=nn1)
@@ -45,14 +45,16 @@ p.s('introduction')
 
 
 con = p.get_new_section_id('Model')
-p.s('Figure 1: flowchart')
+p.s('Figure 1: high-level flowchart')
 
 con = p.get_new_section_id('Software Architecture')
-p.s('Figure 2: structure of code')
+p.s('Figure 2: detailed workflow (including iteration to update posterior)')
 
-con = p.get_new_section_id('Example with diode')
+con = p.get_new_section_id('Example with diode - validation')
+p.s('Figure 3: diode fit stuff')
+
 con = p.get_new_section_id('Example with real data')
-
+p.s('Figure 4: fitting real data (maybe resistive diode?)')
 
 con = p.get_new_section_id('Discussion')
 p.s('discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion ')

### 2018-06-28 paper/manuscript.py
paper outline

@@ -59,13 +59,16 @@ p.s('Figure 4: fitting real data (maybe resistive diode?)')
 con = p.get_new_section_id('Discussion')
 p.s('discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion discussion ')
 
-con = p.get_new_section_id('Conslusions')
+con = p.get_new_section_id('Conclusions')
 p.s('conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions conclusions ')
 
 
 con = p.get_new_section_id('Acknowledgements')
 p.s(r'''acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements acknowledgements ''')
 
+
+con = p.get_new_section_id('Appendix')
+p.s('include minimal code to run diode example')
 
 p.tex()
 p.make('Manuscript',show=True )

### 2018-06-28 paper/Manuscript.tex
updated paper

@@
 %File Generated with PyPaper
-\documentclass[aps,prl,reprint,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress,twocolumn]{revtex4-1}
+\documentclass[aps,prl,reprint,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress]{revtex4-1}
 \usepackage{graphicx}
@@
 \usepackage{stackengine}
+\usepackage[section]{placeins}
 \usepackage[dvipsnames*,svgnames]{xcolor}
@@
 \begin{abstract}
-Achieving low thermal conductivity and good electrical properties is a crucial condition for thermal energy harvesting materials.
-Nanostructuring offers a very powerful tool to address both requirements: in nanostructured materials, boundaries preferentially scatter phonons compared to electrons.
-The search for low-thermal conductivity nanostructures is typically limited to materials with simple crystal structures, such as silicon, because of the complexity arising from modeling branch- and wave vector-dependent nanoscale heat transport.
-Using the phonon mean-free-path (MFP) dependent Boltzmann transport equation, a model that overcomes this limitation, we compute thermal transport in 75 nanoporous Half Heusler compounds for different pore sizes.
-We demonstrate that the optimization of thermal transport in nanostructures should take into account both bulk thermal properties and geometry-dependent phonon suppression, two aspects that are typically engineered separately.
-In fact, our work predicts that, given a set of bulk materials and a system geometry, the ordering of the bulk thermal conductivity does not necessarily align with that of the nanostructure.
-We show that what dictates thermal transport is the interplay between the bulk MFP distribution and the material's characteristic length.
-Finally, we derive a thermal transport model than enables fast systems screening within large bulk material repositories and a given geometry.
-Our study motivates the need for a holistic approach in engineering thermal transport and provides a method for high-throughput materials discovery.\end{abstract}
+abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract \end{abstract}
 \maketitle
 
-\section*{Acknowledgements}
-Research supported as part of the Solid-State Solar-Thermal Energy Conversion Center (S3TEC), an Energy Frontier Research Center funded by the US Department of Energy (DOE), Office of Science, Basic Energy Sciences (BES), under Award DESC0001.\par
-\begin{equation}
-\begin{split}\label{Eq:1001}
-E=mc^2 
-\end{split}
-\end{equation}
+\fakesection{fake}
 
 \section*{Introduction}
-Example of referencens as seen in ~\cite{fugallo2014thermal} and this refers to fig ~\subref*{Fig:10a}referes the Eq. ~(\autoref{Eq:1001}) 
-\begin{figure*}[!ht]
+
+\section*{Model}
+
+\section*{Software Architecture}
+ Figure 1: detailed workflow (including iteration to update posterior)  
+\begin{figure}[!ht]
 
 \subfloat[\label{Fig:10a}]
-{\includegraphics[width=0.48\textwidth]{./figure_1a.png}}
+{\includegraphics[width=0.48\columnwidth]{./figure_1a.png}}
 \hfill
 \subfloat[\label{Fig:10b}]
-{\includegraphics[width=0.48\textwidth]{./figure_1b.png}}
-\caption{}
-\end{figure*}
- %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+{\includegraphics[width=0.48\columnwidth]{./figure_1b.png}}
+\caption{(a) Scheme (b) Probability}
+\end{figure}
+ \begin{figure}
+{\includegraphics[width=0.7\columnwidth]{./figure_2.png}}
+\caption{Bayesian workflow}
+\end{figure}
+\section*{Example with diode - validation}
+ Figure 2: diode fit stuff  \begin{figure}
+{\includegraphics[width=0.7\columnwidth]{./figure_3.png}}
+\caption{Ideal diode}
+\end{figure}
+\section*{Example with real data}
+ Figure 4: fitting real data (maybe resistive diode?)  
+\begin{figure}[!ht]
+
+\subfloat[\label{Fig:40a}]
+{\includegraphics[width=0.48\columnwidth]{./figure_4a.png}}
+\hfill
+\subfloat[\label{Fig:40b}]
+{\includegraphics[width=0.48\columnwidth]{./figure_4b.png}}
+\caption{Real data}
+\end{figure}
+
+\section*{Discussion}
+
+\section*{Conclusions}
+
+\section*{Acknowledgements}
+
+\section*{Appendix}
+ include minimal code to run diode example %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
 %Control: key (0)
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{1}%
+\begin{thebibliography}{0}%
 \makeatletter
@@
 %</preamble>
-\bibitem [{\citenamefont {Fugallo}\ \emph {et~al.}(2014)\citenamefont
-  {Fugallo}, \citenamefont {Cepellotti}, \citenamefont {Paulatto},
-  \citenamefont {Lazzeri}, \citenamefont {Marzari},\ and\ \citenamefont
-  {Mauri}}]{fugallo2014thermal}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Fugallo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Cepellotti}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Paulatto}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Lazzeri}}, \bibinfo {author}
-  {\bibfnamefont {N.}~\bibnamefont {Marzari}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Mauri}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nano letters}\ }\textbf {\bibinfo {volume}
-  {14}},\ \bibinfo {pages} {6109} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
 \end{thebibliography}%

### 2018-06-28 paper/manuscript.py

@@ -1,6 +1,6 @@
 from pypapers.manuscript import Manuscript as M
 
-p = M(biblio_file ='biblio.bib',journal='prl',numberline=False)
+p = M(biblio_file ='biblio.bib',journal='prl',numberline=False,twocolumn=False)
 
 MIT = 'Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'
 
@@ -34,9 +34,8 @@ p.set_title('Byesim: a tool for fast device characterization with Bayesian infer
 
 p.add_abstract_sentence(r'''abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract ''')
 
-con = p.get_new_section_id('Introduction')
+p.new_section('Introduction')
 
-p.s('introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction introduction ')
 #p.s('Example of referencens as seen in ' + p.cite('fugallo2014thermal') + r''' and this refers to fig ''' + p.ref(fig_1 + 'a') + r'''referes the Eq. ''' + p.ref(nn1),br=1)
 
 #p.add_equation(r'''E=mc^2 ''',label=nn1)
@@ -44,30 +43,32 @@ p.s('introduction introduction introduction introduction introduction introducti
 #p.add_figure(filename='figure_1',caption='',label=fig_1,center_page = True)
 
 
-con = p.get_new_section_id('Model')
-p.s('Figure 1: high-level flowchart')
+p.new_section('Model')
+#p.s('Figure 1: high-level flowchart')
 
-con = p.get_new_section_id('Software Architecture')
[…]

### 2018-06-29 paper/Manuscript.tex
fleshing out paper outline a little

@@
 \raggedbottom\usepackage[bottom]{footmisc} \makeatletter \def\p@section{} \def\p@subsubsection{} \makeatother\begin{document}
-\title{Byesim: a tool for fast device characterization with Bayesian inference}
+\title{Bayesim: a tool for fast device characterization with Bayesian inference}
 \author{Rachel Kurchin}
@@
 \begin{abstract}
-abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract \end{abstract}
+Target journal: Computer Physics Communications\end{abstract}
 \maketitle
@@
 \section*{Introduction}
-
+ motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding) 
 \section*{Model}
-
-\section*{Software Architecture}
- Figure 1: detailed workflow (including iteration to update posterior)  
+ \begin{itemize}\item background on Bayes theorem \item particulars about how it can be applied to fitting problems we're interested in \item advantages over traditional fitting approaches \item figure 1 \end{itemize}
 \begin{figure}[!ht]
@@
 \end{figure}
- \begin{figure}
+
+\section*{Software Architecture and Interface}
+ \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
 {\includegraphics[width=0.7\columnwidth]{./figure_2.png}}
@@
 \end{figure}
-\section*{Example with diode - validation}
- Figure 2: diode fit stuff  \begin{figure}
+\section*{Application Examples}
+ \subsection{Ideal Diode Model} \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
 {\includegraphics[width=0.7\columnwidth]{./figure_3.png}}
 \caption{Ideal diode}
-\end{figure}
-\section*{Example with real data}
- Figure 4: fitting real data (maybe resistive diode?)  
+\end{figure}\subsection{Example with Real Data} \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}
 \begin{figure}[!ht]
@@
 \end{figure}
-
-\section*{Discussion}
-
+\subsection{Maybe an example with a numerical model like PC1D} \subsection{Maybe a non-PV example} thermoelectrics? TIDLS? 
 \section*{Conclusions}
@@
 \section*{Appendix}
- include minimal code to run diode example %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+ \begin{itemize}\item include minimal code to run ideal diode example \item link to Github repo (which has installation instructions and documentation as well as list of planned future features) \end{itemize} %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
 %Control: key (0)

### 2018-06-29 paper/manuscript.py

@@ -30,12 +30,13 @@ p.add_alias(r'''\alpha_{\mathrm{bulk}}''','abulk')
 p.add_alias(r'''\mathbf{\hat{s}}''','s')
 
 
-p.set_title('Byesim: a tool for fast device characterization with Bayesian inference')
+p.set_title('Bayesim: a tool for fast device characterization with Bayesian inference')
 
-p.add_abstract_sentence(r'''abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract ''')
+p.add_abstract_sentence(r'''Target journal: Computer Physics Communications''')
 
 p.new_section('Introduction')
 
+p.s('motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding)')
 #p.s('Example of referencens as seen in ' + p.cite('fugallo2014thermal') + r''' and this refers to fig ''' + p.ref(fig_1 + 'a') + r'''referes the Eq. ''' + p.ref(nn1),br=1)
 
 #p.add_equation(r'''E=mc^2 ''',label=nn1)
@@ -44,23 +45,29 @@ p.new_section('Introduction')
 
 
 p.new_section('Model')
-#p.s('Figure 1: high-level flowchart')
-
-p.new_section('Software Architecture')
-p.s('Figure 1: detailed workflow (including iteration to update posterior)')
+p.s(r'''\begin{itemize}\item background on Bayes theorem \item particulars about how it can be applied to fitting problems we're interested in \item advantages over traditional fitting approaches \item figure 1 \end{itemize}''')
 
 p.add_figure(filename='figure_1',caption='(a) Scheme (b) Probability',center_page = False,label=fig_1)
+
+p.new_section('Software Architecture and Interface')
[…]

### 2018-06-29 paper/Manuscript.tex
updated paper

@@
 \section*{Model}
- \begin{itemize}\item background on Bayes theorem \item particulars about how it can be applied to fitting problems we're interested in \item advantages over traditional fitting approaches \item figure 1 \end{itemize}
+ \begin{itemize}
+ \item background on Bayes theorem
+ \item particulars about how it can be applied to fitting problems we're interested in
+ \item advantages over traditional fitting approaches
+ \item figure 1
+ \end{itemize}
+
 \begin{figure}[!ht]
@@
 \subfloat[\label{Fig:10a}]
-{\includegraphics[width=0.48\columnwidth]{./figure_1a.png}}
+{\includegraphics[width=0.48\columnwidth]{././figure_1a.png}}
 \hfill
 \subfloat[\label{Fig:10b}]
-{\includegraphics[width=0.48\columnwidth]{./figure_1b.png}}
+{\includegraphics[width=0.48\columnwidth]{././figure_1b.png}}
 \caption{(a) Scheme (b) Probability}
@@
  \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
-{\includegraphics[width=0.7\columnwidth]{./figure_2.png}}
+{\includegraphics[width=0.7\columnwidth]{././figure_2.png}}
 \caption{Bayesian workflow}
@@
 \section*{Application Examples}
- \subsection{Ideal Diode Model} \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
-{\includegraphics[width=0.7\columnwidth]{./figure_3.png}}
+ \subsection{Ideal Diode Model}
+  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
+{\includegraphics[width=0.7\columnwidth]{././figure_3.png}}
 \caption{Ideal diode}
-\end{figure}\subsection{Example with Real Data} \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}
+\end{figure}\subsection{Example with Real Data}
+  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}
 \begin{figure}[!ht]
@@
 \subfloat[\label{Fig:40a}]
-{\includegraphics[width=0.48\columnwidth]{./figure_4a.png}}
+{\includegraphics[width=0.48\columnwidth]{././figure_4a.png}}
 \hfill
 \subfloat[\label{Fig:40b}]
-{\includegraphics[width=0.48\columnwidth]{./figure_4b.png}}
+{\includegraphics[width=0.48\columnwidth]{././figure_4b.png}}
 \caption{Real data}
 \end{figure}
-\subsection{Maybe an example with a numerical model like PC1D} \subsection{Maybe a non-PV example} thermoelectrics? TIDLS? 
+\subsection{Maybe an example with a numerical model like PC1D}
+  \subsection{Maybe a non-PV example}
+  thermoelectrics? TIDLS? 
 \section*{Conclusions}

### 2018-06-29 paper/manuscript.py

@@ -34,7 +34,7 @@ p.set_title('Bayesim: a tool for fast device characterization with Bayesian infe
 
 p.add_abstract_sentence(r'''Target journal: Computer Physics Communications''')
 
-p.new_section('Introduction')
+p.section('Introduction')
 
 p.s('motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding)')
 #p.s('Example of referencens as seen in ' + p.cite('fugallo2014thermal') + r''' and this refers to fig ''' + p.ref(fig_1 + 'a') + r'''referes the Eq. ''' + p.ref(nn1),br=1)
@@ -44,38 +44,46 @@ p.s('motivation (within PV and beyond) citing examples of our application of thi
 #p.add_figure(filename='figure_1',caption='',label=fig_1,center_page = True)
 
 
-p.new_section('Model')
-p.s(r'''\begin{itemize}\item background on Bayes theorem \item particulars about how it can be applied to fitting problems we're interested in \item advantages over traditional fitting approaches \item figure 1 \end{itemize}''')
+p.section('Model')
 
-p.add_figure(filename='figure_1',caption='(a) Scheme (b) Probability',center_page = False,label=fig_1)
+s1 =  'background on Bayes theorem'
+s2 =  r'''particulars about how it can be applied to fitting problems we're interested in'''
+s3 = 'advantages over traditional fitting approaches'
+s4 =  'figure 1'
+p.itemize([s1,s2,s3,s4])
 
-p.new_section('Software Architecture and Interface')
+
+
+
+p.figure(filename='figure_1',caption='(a) Scheme (b) Probability',center_page = False,label=fig_1)
+
+p.section('Software Architecture and Interface')
 p.s(r'''\begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}''')
 
-p.add_figure(filename='figure_2',caption='Bayesian workflow',center_page = False,label = fig_2)
+p.figure(filename='figure_2',caption='Bayesian workflow',center_page = False,label = fig_2)
 
-con = p.new_section('Application Examples')
+p.section('Application Examples')
+p.subsection('Ideal Diode Model')
 
-p.s(r'''\subsection{Ideal Diode Model}''')
[…]

### 2018-06-29 paper/Manuscript.tex
add doc

@@
 \usepackage{mathtools}
+\usepackage{todonotes}
 \usepackage{amsmath}
@@
 \end{figure}\subsection{Example with Real Data}
-  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}
+  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize} \todo[inline]{example fgryer2qt rt r}
 \begin{figure}[!ht]

### 2018-06-29 bayesim/model.py
working on closing the subdivide loop

@@ -8,19 +8,10 @@ import numpy as np
 class model(object):
     """
     Updates from 180626 meeting:
-        top priorities: accepting files as input, saving state (everything else later)
-
         make subdivide, visualize methods here
-        m= bayesim(load_state=True,filename='')
-        create mocked data (diode) for model and obs in hdf5 format (so GR can use it for the command line version)
-        add option to run() for how often to save intermediate PMFs
-        maybe also a boolean for whether it's waiting for new model data
         create new internal variable new_sims_list or something
         also add a method to return new_sims_list either as df or write to file, etc.
         fix inputs to different functions (messy)
-        make sure everything can accept files as inputs (important for argparse)
-        add save_state function that writes hdf5 with all current variables
-        maybe make entire state into a dict?
 
     Todo:
         animating visualization during run
@@ -215,10 +206,10 @@ class model(object):
             gb (:obj:`groupby`): Pandas groupby object of model data grouped by parameter points
         """
         grps = argv['gb']
-        ec_pts = pd.DataFrame.from_records(data=self.obs_data.groupby(self.ec).groups.keys(),columns=self.ec).round(self.ec_tol_digits).sort_values(ec).reset_index(drop=True)
+        ec_pts = pd.DataFrame.from_records(data=self.obs_data.groupby(self.ec).groups.keys(),columns=self.ec).round(self.ec_tol_digits).sort_values(self.ec).reset_index(drop=True)
         # then check at each model point that they match
         for name,group in grps:
-            if not all(ec_pts==group.round(self.ec_tol_digits).sort_values(ec).reset_index(drop=True)):
+            if not all(ec_pts==group[self.ec].round(self.ec_tol_digits).sort_values(self.ec).reset_index(drop=True)):
                 raise ValueError('The experimental conditions do not match to %d digits between the observed and modeled data at the modeled parameter space point %s!'%(self.ec_tol_digits,name))
                 return
 
@@ -234,6 +225,7 @@ class model(object):
         Todo:
             Should adding additional model data be a separate function?
             some way to elegantly use the function when adding new model data?
+            pmf should maybe store start/end indices, either way split out computing them rather than copying code!
         """
 
         #mode = argv.setdefault('mode','file')
@@ -249,7 +241,7 @@ class model(object):
 
             # next get list of parameter space points
             param_points_grps = self.model_data.groupby(self.param_names)
[…]

### 2018-07-02 bayesim/model.py
adding new sims is working, starting on gradient calc

@@ -209,7 +209,7 @@ class model(object):
         ec_pts = pd.DataFrame.from_records(data=self.obs_data.groupby(self.ec).groups.keys(),columns=self.ec).round(self.ec_tol_digits).sort_values(self.ec).reset_index(drop=True)
         # then check at each model point that they match
         for name,group in grps:
-            if not all(ec_pts==group[self.ec].round(self.ec_tol_digits).sort_values(self.ec).reset_index(drop=True)):
+            if not all(ec_pts==group[['V','T']].round(self.ec_tol_digits).sort_values(self.ec).reset_index(drop=True)):
                 raise ValueError('The experimental conditions do not match to %d digits between the observed and modeled data at the modeled parameter space point %s!'%(self.ec_tol_digits,name))
                 return
 
@@ -294,6 +294,7 @@ class model(object):
                 end_ind = subset.index[-1]+1
                 self.start_indices.append(start_ind)
                 self.end_indices.append(end_ind)
+
         elif mode=='add':
             # import and sort data
             new_data = dd.io.load(argv['fpath']).sort_values(self.param_names)
@@ -330,11 +331,16 @@ class model(object):
                     query_str = query_str + 'abs(%f-%s)/%s<1e-6 & '%(param_vals[n],n,n)
                 query_str = query_str[:-3]
 
-                subset = self.model_data.tail(len(new_data)).query(query_str)
+                #subset = self.model_data.tail(len(new_data)).query(query_str)
+                subset = self.model_data.query(query_str) # slower but won't miss anything
+                if len(subset)==0:
+                    print('Something went wrong calculating sim indices! Could not find any points in model data for params %s.'%query_str)
                 start_ind = subset.index[0]
                 end_ind = subset.index[-1]+1
                 self.start_indices.append(start_ind)
                 self.end_indices.append(end_ind)
+            self.needs_new_model_data = False
+
 
         elif mode=='function':
             # is there a way to save this (that could be saved to HDF5 too) so that subdivide can automatically call it?
@@ -420,6 +426,8 @@ class model(object):
         save_step = argv.setdefault('save_step',10)
         th_pm = argv.setdefault('th_pm',0.8)
         th_pv = argv.setdefault('th_pv',0.05)
+        th_pm = argv['th_pm']
+        th_pv = argv['th_pv']
         # need to test whether I need to specifically parse into the namespace if they're different from defaults
 
[…]

### 2018-07-02 bayesim/test_grad_calc.py

@@ -1,0 +1,10 @@
+import numpy as np
+
+mat = np.random.randint(low=0,high=100,size=(5,5))
+mat
+
+mat.shape
+
+deltas = {}
+for i in range(len(mat.shape)):
+    

### 2018-08-21 paper/manuscript.py
working on manuscript

@@ -1,6 +1,6 @@
 from pypapers.manuscript import Manuscript as M
 
-p = M(biblio_file ='biblio.bib',journal='prl',numberline=False,twocolumn=False)
+p = M(biblio_file ='biblio.bib', journal='prl', numberline=False, twocolumn=False)
 
 MIT = 'Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'
 
@@ -36,42 +36,58 @@ p.add_abstract_sentence(r'''Target journal: Computer Physics Communications''')
 
 p.section('Introduction')
 
-p.s('motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding)')
-#p.s('Example of referencens as seen in ' + p.cite('fugallo2014thermal') + r''' and this refers to fig ''' + p.ref(fig_1 + 'a') + r'''referes the Eq. ''' + p.ref(nn1),br=1)
+#p.s('motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding), add some stuff about how semiconductor device community lags behind many others in model tuning, etc.')
+p.s('There are a plethora of examples across diverse scientific and engineering fields of mathematical models used to simulate the results of experimental observations. In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters. Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.')
 
-#p.add_equation(r'''E=mc^2 ''',label=nn1)
[…]

### 2018-08-21 paper/Manuscript.tex
paper updated

--- 2018-06-29 paper/Manuscript.tex
@@
 %File Generated with PyPaper
-\documentclass[aps,prl,reprint,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress]{revtex4-1}
+\documentclass[aps,prl,amsmath,amssymb,superscriptaddress,notitlepage,groupedaddress]{revtex4-1}
 \usepackage{graphicx}
@@
 \section*{Introduction}
- motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding) 
+ There are a plethora of examples across diverse scientific and engineering fields of mathematical models used to simulate the results of experimental observations.
+In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters.
+Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.
+We have previously demonstrated the value of a Bayesian approach in using automated high-throughput temperature- and illumination-dependent current-voltage measurements (JVTi) to fit material/interface properties and defect recombination parameters in photovoltaic (PV) absorbers~\cite{SnSJoule,FeBayes}.
+In cases such as these, when the data model is not a simple analytical equation but rather a computationally intensive numerical model, efficient, nonredundant sampling of the parameter space when computing likelihoods becomes critical to making the fit feasible.
+In this work, we introduce 	exttt{bayesim}, a Python-based code that utilizes adaptive grid sampling to perform Bayesian parameter estimation.
+We discuss the structure of the code, its implementation, and provide several examples of its usage.
+While the authors' expertise is in the realm of semiconductor physics and thus the examples herein are drawn from that space, we also discuss the general characteristics of a problem amenable to this approach so that researchers from other fields might adopt it as well.
 \section*{Model}
- \begin{itemize}
- \item background on Bayes theorem
- \item particulars about how it can be applied to fitting problems we're interested in
- \item advantages over traditional fitting approaches
- \item figure 1
- \end{itemize}
-
-\begin{figure}[!ht]
-
-\subfloat[\label{Fig:10a}]
-{\includegraphics[width=0.48\columnwidth]{././figure_1a.png}}
-\hfill
-\subfloat[\label{Fig:10b}]
-{\includegraphics[width=0.48\columnwidth]{././figure_1b.png}}
-\caption{(a) Scheme (b) Probability}
-\end{figure}
-
+ \todo[inline]{Should this section titel actually just be ``Technical Background`` as well perhaps?} Bayes' Theorem states \begin{equation}
+\begin{split}\label{Eq:1001}
+P(H|E)=\frac{P(H)P(E|H)}{P(E)}
+\end{split}
+\end{equation}
+where $H$ is a \textit{hypothesis} and $E$ the observed \textit{evidence}.
+$P(H)$ is termed the \textit{prior}, $P(E|H)$ the \textit{likelihood}, $P(H|E)$ the \textit{posterior}, and $P(E)$ is a normalizing constant.
+If there are $n$ pieces of evidence, this can generalize to an iterative process where \begin{equation}
+\begin{split}\label{Eq:2}
+P(H|\{E_1,E_2,...E_n\}) = \frac{P(H|\{E_1,E_2...E_{n-1}\})P(E_n|H)}{P(E_n)}
+\end{split}
+\end{equation}
+In a multidimensional parameter estimation problem, each hypothesis $H$ is a tuple of possible values for the fitting parameters, i.e.
+a point in the parameter space.
+In \texttt{bayesim}, likelihoods are calculated for each point using a Gaussian where the argument is the difference between observed and simulated output and the standard deviation is the sum of experimental uncertainty and model uncertainty.
+The experimental uncertainty is a number provided by the user, while the model uncertainty is calculated by \texttt{bayesim} and reflects the sparseness of the parameter space grid, i.e.
+how much simulated output changes from one grid point to another.
+A high-level flowchart of what \texttt{bayesim} does is shown in ~(\autoref{fig_1})a.
 \section*{Software Architecture and Interface}
- \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
-{\includegraphics[width=0.7\columnwidth]{././figure_2.png}}
-\caption{Bayesian workflow}
-\end{figure}
+ \subsection{Structure}
+  The structure of \texttt{bayeim} is shown in ~(\autoref{fig_2}).
+The top-level object with which users interact is implemented in the \texttt{Model} class.
+The \texttt{params} module defines classes to store information about the various types of parameters (fitting parameters, experimental conditions, and measured output) while the \texttt{Pmf} class stores the probability distribution and implements the manipulations required for Bayesian updates.
+\subsection{Interfaces}
+  describe ways to "talk to" \texttt{bayesim}. \subsection{Dependencies}
+  \todo[inline]{This probably makes sense to include also, right?} 
 \section*{Application Examples}
  \subsection{Ideal Diode Model}
-  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
-{\includegraphics[width=0.7\columnwidth]{././figure_3.png}}
-\caption{Ideal diode}
-\end{figure}\subsection{Example with Real Data}
-  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}
-\begin{figure}[!ht]
-
-\subfloat[\label{Fig:40a}]
-{\includegraphics[width=0.48\columnwidth]{././figure_4a.png}}
-\hfill
-\subfloat[\label{Fig:40b}]
-{\includegraphics[width=0.48\columnwidth]{././figure_4b.png}}
-\caption{Real data}
-\end{figure}
-\subsection{Maybe an example with a numerical model like PC1D}
+  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF \end{itemize}  \subsection{Example with Real Data}
+  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}  \subsection{Maybe an example with a numerical model like PC1D}
   \subsection{Maybe a non-PV example}
@@
 \section*{Conclusions}
-
+ talk about broader applicability of approach 
 \section*{Acknowledgements}
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{0}%
+\begin{thebibliography}{2}%
 \makeatletter
@@
 %</preamble>
+\bibitem [{\citenamefont {Brandt}\ \emph {et~al.}(2017)\citenamefont {Brandt},
+  \citenamefont {Kurchin}, \citenamefont {Steinmann}, \citenamefont {Kitchaev},
+  \citenamefont {Roat}, \citenamefont {Levcenco}, \citenamefont {Ceder},
+  \citenamefont {Unold}, \citenamefont {Buonassisi},\ and\ \citenamefont
+  {Berlin}}]{SnSJoule}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~E.}\ \bibnamefont
+  {Brandt}}, \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont {Kurchin}},
+  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Steinmann}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Kitchaev}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Roat}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Levcenco}}, \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {Ceder}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Unold}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Buonassisi}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {H.~Z.}\ \bibnamefont {Berlin}},\ }\href {\doibase
+  10.1016/j.joule.2017.10.001} {\bibfield  {journal} {\bibinfo  {journal}
+  {Joule}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {843} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kurchin}\ \emph {et~al.}(2018)\citenamefont
+  {Kurchin}, \citenamefont {Poindexter}, \citenamefont {Kitchaev},
+  \citenamefont {V\"ah\"anissi}, \citenamefont {del Ca\~nizo}, \citenamefont
+  {Zhe}, \citenamefont {Laine}, \citenamefont {Roat}, \citenamefont {Levcenco},
+  \citenamefont {Ceder},\ and\ \citenamefont {Buonassisi}}]{FeBayes}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
+  {Kurchin}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Poindexter}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Kitchaev}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {V\"ah\"anissi}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {del
+  Ca\~nizo}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zhe}},
+  \bibinfo {author} {\bibfnamefont {H.~S.}\ \bibnamefont {Laine}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Roat}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Levcenco}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Ceder}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Buonassisi}},\ }\href@noop {} {\enquote
+  {\bibinfo {title} {Semiconductor parameter extraction via current-voltage
+  characterization and bayesian inference methods},}\ } (\bibinfo {year}
+  {2018})\BibitemShut {NoStop}%
 \end{thebibliography}%

### 2018-08-21 paper/manuscript.py

@@ -5,9 +5,9 @@ p = M(biblio_file ='biblio.bib', journal='prl', numberline=False, twocolumn=Fals
 MIT = 'Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'
 
 
-p.add_author('Rachel Kurchin',[MIT])
-p.add_author('Giuseppe Romano',[MIT])
-p.add_author('Tonio Buonassisi',[MIT],email='buonassi@mit.edu')
+p.author('Rachel Kurchin',[MIT])
+p.author('Giuseppe Romano',[MIT])
+p.author('Tonio Buonassisi',[MIT],email='buonassi@mit.edu')
 
 
 fig_1 = p.get_new_figure_label()
@@ -20,19 +20,12 @@ nn2 = p.get_new_equation_label()
 nn3 = p.get_new_equation_label()
 nn4 = p.get_new_equation_label()
 
-p.add_alias(r'''\kappa_{\mathrm{eff}}''','keff')
-p.add_alias(r'''\mathbf{\hat{x}}''','x')
-p.add_alias(r'''\kappa_{\mathrm{bulk}}''','kbulk')
-p.add_alias(r'''K_{\mathrm{bulk}}''','Kbulk')
-p.add_alias(r'''\tilde{\kappa}_{\mathrm{eff}}''','ktilde')
-p.add_alias(r'''\kappa_{\mathrm{Fourier}}''','kfourier')
-p.add_alias(r'''\alpha_{\mathrm{bulk}}''','abulk')
-p.add_alias(r'''\mathbf{\hat{s}}''','s')
+p.alias(r'''\kappa_{\mathrm{eff}}''','keff')
 
 
-p.set_title('Bayesim: a tool for fast device characterization with Bayesian inference')
+p.title('Bayesim: a tool for fast device characterization with Bayesian inference')
 
-p.add_abstract_sentence(r'''Target journal: Computer Physics Communications''')
+p.abstract(r'''Target journal: Computer Physics Communications''')
 
 p.section('Introduction')
 
@@ -49,34 +42,33 @@ p.note('Should this section titel actually just be ``Technical Background`` as w
 
 p.s("Bayes' Theorem states")
 
-p.add_equation('P(H|E)=\frac{P(H)P(E|H)}{P(E)}')
+p.equation(r'''P(H|E)=\frac{P(H)P(E|H)}{P(E)}''',label=nn1)
 
[…]

### 2018-08-21 paper/manuscript.py
still doesn't compile...

@@ -2,12 +2,12 @@ from pypapers.manuscript import Manuscript as M
 
 p = M(biblio_file ='biblio.bib', journal='prl', numberline=False, twocolumn=False)
 
-MIT = 'Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'
+DMSE = r'''Department of Materials Science \& Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'''
+MechE = r'''Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'''
 
-
-p.author('Rachel Kurchin',[MIT])
-p.author('Giuseppe Romano',[MIT])
-p.author('Tonio Buonassisi',[MIT],email='buonassi@mit.edu')
+p.author(r'''Rachel Kurchin''',[DMSE])
+p.author('Giuseppe Romano',[MechE])
+p.author('Tonio Buonassisi',[MechE], email='buonassi@mit.edu')
 
 
 fig_1 = p.get_new_figure_label()

### 2018-08-22 paper/Manuscript.tex
test
switching over to TeX rather than pypapers

--- 2018-06-29 paper/Manuscript.tex
@@
 \raggedbottom\usepackage[bottom]{footmisc} \makeatletter \def\p@section{} \def\p@subsubsection{} \makeatother\begin{document}
-\title{Bayesim: a tool for fast device characterization with Bayesian inference}
+\title{\texttt{bayesim}: a tool for fast model fitting with Bayesian inference}
 \author{Rachel Kurchin}
-\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\affiliation{Department of Materials Science \& Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
 \author{Giuseppe Romano}
@@
 \section*{Introduction}
- motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding) 
+  There are a plethora of examples across diverse scientific and engineering fields of mathematical models used to simulate the results of experimental observations.
+In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters.
+Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.
+
+  We have previously demonstrated the value of a Bayesian approach in using automated high-throughput temperature- and illumination-dependent current-voltage measurements (JVTi) to fit material/interface properties and defect recombination parameters in photovoltaic (PV) absorbers~\cite{SnSJoule,FeBayes}.
+In cases such as these, when the data model is not a simple analytical equation but rather a computationally intensive numerical model, efficient, nonredundant sampling of the parameter space when computing likelihoods becomes critical to making the fit feasible.
+
+  In this work, we introduce \texttt{bayesim}, a Python-based code that utilizes adaptive grid sampling to perform Bayesian parameter estimation.
+We discuss the structure of the code, its implementation, and provide several examples of its usage.
+While the authors' expertise is in the realm of semiconductor physics and thus the examples herein are drawn from that space, we also discuss the general characteristics of a problem amenable to this approach so that researchers from other fields might adopt it as well.
+
 \section*{Model}
+  \todo[inline]{Should this section title actually just be ``Technical Background`` as well perhaps?}
+
+ Bayes' Theorem is a relationship between conditional probabilities. It states
+
+ \begin{equation}
+   \begin{split}
+     \label{Eq:1001}
+     P(H|E)=\frac{P(H)P(E|H)}{P(E)}
+   \end{split}
+ \end{equation}
+
+ where the notation $P(A|B)$ indicates the probability of $A$ being true given that $B$ is true.
+$H$ is a \textit{hypothesis} and $E$ the observed \textit{evidence}.
+$P(H)$ is termed the \textit{prior}, $P(E|H)$ the \textit{likelihood}, $P(H|E)$ the \textit{posterior}, and $P(E)$ is a normalizing constant.
+If there are $n$ pieces of evidence, this can generalize to an iterative process where
+
+ \begin{equation}
+   \begin{split}
+     \label{Eq:2}
+     P(H|\{E_1,E_2,...E_n\}) = \frac{P(H|\{E_1,E_2...E_{n-1}\})P(E_n|H)}{P(E_n)}
+   \end{split}
+ \end{equation}
+
+ In a multidimensional parameter estimation problem, each hypothesis $H$ is a tuple of possible values for the fitting parameters, i.e.
+a point in the parameter space, while the evidence $E$ is an observed output of a measurement as a function of various experimental conditions.
+
+ In order to compute a likelihood, a model capable of simulating that observed output as a function of both the fitting parameters and the experimental conditions is required.
+In \texttt{bayesim}, likelihoods are calculated for each point in parameter space using a Gaussian where the argument is the difference between observed and simulated output at that point, and the standard deviation is the sum of experimental uncertainty and model uncertainty.
+The experimental uncertainty is a number provided by the user that quantifies any noise/irreproducibility inherent to the measurement, while the model uncertainty is calculated by \texttt{bayesim} and reflects the sparseness of the parameter space grid, i.e.
+how much simulated output changes from one grid point to another.
+
+ \begin{figure}
+   {\includegraphics[width=0.7\columnwidth]{././figure_1.png}}
+   \caption{(Figure copied from docs website for now, will make a publication-appropriate version)}
+ \end{figure}
+
+ A high-level summary of what \texttt{bayesim} does is shown in Figure~\subref*{Fig:10}.
+Part a is a flowchart showing that observed (as a function of experimental conditions $\{C\}$ and simulated (as a function of fitting parameters $\{P\}$ and experimental conditions $\{C\}$) outputs are compared to produce a probability distribution over $\{P\}$.
+Part b schematically indicates the adaptive grid sampling approach for a hypothetical two-dimensional parameter space, wherein grid boxes exceeding some threshold probability are subdivided and lower-probability regions discarded, allowing attainment of a high fitting precision without needing to sample the entire parameter space at the same high density.
+
+\section*{Software Architecture and Interface}
+  \subsection{Structure}
+    The structure of \texttt{bayeim} is shown in ~(\autoref{fig_2}).
+The top-level object with which users interact is implemented in the \texttt{Model} class.
+The \texttt{params} module defines classes to store information about the various types of parameters (fitting parameters, experimental conditions, and measured output) while the \texttt{Pmf} class stores the probability distribution and implements the manipulations required for Bayesian updates.
+
+  \subsection{Interfaces}
+    describe ways to ``talk to'' \texttt{bayesim}.
+
+  \subsection{Dependencies}
+    \todo[inline]{This probably makes sense to include also, right?}
+
+\section*{Application Examples}
+  \subsection{Ideal Diode Model}
     \begin{itemize}
- \item background on Bayes theorem
- \item particulars about how it can be applied to fitting problems we're interested in
- \item advantages over traditional fitting approaches
- \item figure 1
+      \item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters
+      \item figure 3 showing PMF
     \end{itemize}
 
-\begin{figure}[!ht]
+  \subsection{Example with Real Data}
+    \begin{itemize}
+      \item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper
+      \item figure 4 showing PMF (animation in ESI) and comparison of JV curves
+    \end{itemize}
 
-\subfloat[\label{Fig:10a}]
-{\includegraphics[width=0.48\columnwidth]{././figure_1a.png}}
-\hfill
-\subfloat[\label{Fig:10b}]
-{\includegraphics[width=0.48\columnwidth]{././figure_1b.png}}
-\caption{(a) Scheme (b) Probability}
-\end{figure}
+  \subsection{Maybe an example with a numerical model like PC1D}
 
-\section*{Software Architecture and Interface}
- \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
-{\includegraphics[width=0.7\columnwidth]{././figure_2.png}}
-\caption{Bayesian workflow}
-\end{figure}
-\section*{Application Examples}
- \subsection{Ideal Diode Model}
-  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
-{\includegraphics[width=0.7\columnwidth]{././figure_3.png}}
-\caption{Ideal diode}
-\end{figure}\subsection{Example with Real Data}
-  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}
-\begin{figure}[!ht]
-
-\subfloat[\label{Fig:40a}]
-{\includegraphics[width=0.48\columnwidth]{././figure_4a.png}}
-\hfill
-\subfloat[\label{Fig:40b}]
-{\includegraphics[width=0.48\columnwidth]{././figure_4b.png}}
-\caption{Real data}
-\end{figure}
-\subsection{Maybe an example with a numerical model like PC1D}
   \subsection{Maybe a non-PV example}
     thermoelectrics? TIDLS?
+
 \section*{Conclusions}
+ talk about broader applicability of approach
 
@@
 \section*{Appendix}
- \begin{itemize}\item include minimal code to run ideal diode example \item link to Github repo (which has installation instructions and documentation as well as list of planned future features) \end{itemize} %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (8) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
-\begin{thebibliography}{0}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\end{thebibliography}%
+ \begin{itemize}
+   \item include minimal code to run ideal diode example
+   \item link to Github repo (which has installation instructions and documentation as well as list of planned future features)
+  \end{itemize}
+
+\bibliography{biblio}
+\bibliographystyle{ieeetr}
+
 \end{document}

### 2018-08-22 paper/manuscript.py

@@ -23,36 +23,39 @@ nn4 = p.get_new_equation_label()
 p.alias(r'''\kappa_{\mathrm{eff}}''','keff')
 
 
-p.title('Bayesim: a tool for fast device characterization with Bayesian inference')
+p.title(r'''\texttt{bayesim}: a tool for fast model fitting with Bayesian inference''')
 
 p.abstract(r'''Target journal: Computer Physics Communications''')
 
 p.section('Introduction')
 
 #p.s('motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding), add some stuff about how semiconductor device community lags behind many others in model tuning, etc.')
-p.s('There are a plethora of examples across diverse scientific and engineering fields of mathematical models used to simulate the results of experimental observations. In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters. Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.')
+p.s('There are a plethora of examples across diverse scientific and engineering fields of mathematical models used to simulate the results of experimental observations. In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters. Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.', br=True)
 
[…]

### 2018-08-22 paper/Manuscript.tex
first couple sections done

@@
 \newcommand {\framedgraphic}[2] {\begin{frame}{#1}\begin{center}\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{#2}\end{center}\end{frame}}\usepackage[breaklinks]{hyperref}
-\usepackage{breakurl}
 \usepackage{tabularx}
@@
 \affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+
 \begin{abstract}
-Target journal: Computer Physics Communications\end{abstract}
+Target journal: Computer Physics Communications
+\end{abstract}
+
 \maketitle
-
-\fakesection{fake}
 
@@
  \begin{figure}
-   {\includegraphics[width=0.7\columnwidth]{././figure_1.png}}
+   \includegraphics[width=0.7\columnwidth]{figure_1.png}
    \caption{(Figure copied from docs website for now, will make a publication-appropriate version)}
+   \label{fig1}
  \end{figure}
 
- A high-level summary of what \texttt{bayesim} does is shown in Figure~\subref*{Fig:10}.
-Part a is a flowchart showing that observed (as a function of experimental conditions $\{C\}$ and simulated (as a function of fitting parameters $\{P\}$ and experimental conditions $\{C\}$) outputs are compared to produce a probability distribution over $\{P\}$.
-Part b schematically indicates the adaptive grid sampling approach for a hypothetical two-dimensional parameter space, wherein grid boxes exceeding some threshold probability are subdivided and lower-probability regions discarded, allowing attainment of a high fitting precision without needing to sample the entire parameter space at the same high density.
+ A high-level summary of what \texttt{bayesim} does is shown in ~\autoref{fig1}.
+Part (a) is a flowchart showing that observed (as a function of experimental conditions $\{C\}$ and simulated (as a function of fitting parameters $\{P\}$ and experimental conditions $\{C\}$) outputs are compared to produce a probability distribution over $\{P\}$.
+Part (b) schematically indicates the adaptive grid sampling approach for a hypothetical two-dimensional parameter space, wherein grid boxes exceeding some threshold probability are subdivided and lower-probability regions discarded, allowing attainment of a high fitting precision without needing to sample the entire parameter space at the same high density.
 
 \section*{Software Architecture and Interface}
+
+  \begin{figure}
+    \includegraphics[width=0.7\columnwidth]{structure.png}
+    \caption{\texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces.}
+    \label{structure}
+  \end{figure}
+
+  The structure of \texttt{bayeim} is shown in ~\autoref{structure}. Detailed and up-to-date documentation of classes, functions, and example applications is maintained online.~\cite{docs}
+
   \subsection{Structure}
-    The structure of \texttt{bayeim} is shown in ~(\autoref{fig_2}).
+
     The top-level object with which users interact is implemented in the \texttt{Model} class.
@@
   \subsection{Interfaces}
-    describe ways to ``talk to'' \texttt{bayesim}.
+    The most flexible way to interact with \texttt{bayesim} is via Python scripting or through literate programming in a Jupyter notebook.
+There is also a command line interface (CLI) for users less familiar with coding in Python.
 
   \subsection{Dependencies}
-    \todo[inline]{This probably makes sense to include also, right?}
+    \texttt{bayesim} relies on a variety of external open-source packages.
+These include \texttt{numpy}~\cite{numpy} and \texttt{scipy}~\cite{scipy} for a variety of mathematical functions and vectorized implementations, \texttt{joblib}~\cite{joblib} for simple parallelism, \texttt{deepdish}~\cite{deepdish} for saving and loading HDF5 files, \texttt{pandas}~\cite{pandas} for data manipulation, and \texttt{matplotlib}~\cite{mpl} for visualization.
 
@@
 
-  \subsection{Example with Real Data}
+  \subsection{SnS Solar Cell}
     \begin{itemize}
-      \item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper
-      \item figure 4 showing PMF (animation in ESI) and comparison of JV curves
+      \item more practical example - replicating fit from Joule paper
+      \item figure 4 showing PMF and comparison of JV curves
     \end{itemize}
-
-  \subsection{Maybe an example with a numerical model like PC1D}
-
-  \subsection{Maybe a non-PV example}
-    thermoelectrics? TIDLS?
 

### 2018-08-22 bayesim/model.py

@@ -1,5 +1,6 @@
 from bayesim.pmf import Pmf
 import bayesim.params as pm
+from bayesim.utils import calc_deltas
 import pandas as pd
 import deepdish as dd
 from copy import deepcopy
@@ -10,58 +11,6 @@ import os
 import sys
 from joblib import Parallel, delayed, cpu_count
 import time
-
-def calc_deltas(grp, inds, param_lengths, model_data, fit_param_names, probs, output_var):
-    # construct matrix of output_var({fit_params})
-    subset = deepcopy(model_data.loc[inds])
-    # sort and reset index of subset to match probs so we can use the find_neighbor_boxes function if needed
-    subset.drop_duplicates(subset=fit_param_names, inplace=True)
-    subset.sort_values(fit_param_names, inplace=True)
-    subset.reset_index(inplace=True)
-    if not len(subset.index)==len(probs.points.index):
-        raise ValueError("Subset at EC's %s does not match probability grid!"%str(grp))
-
-    # check if on a grid
-    if not len(subset)==np.product(param_lengths):
-        is_grid = False
-        # construct grid at the highest level of subdivision
-        dense_grid = probs.populate_dense_grid(df=subset, col_to_pull=output_var, make_ind_lists=True)
-        mat = dense_grid['mat']
-        ind_lists = dense_grid['ind_lists']
-
-    else:
-        is_grid = True
-        mat = np.reshape(list(subset[output_var]), param_lengths)
-
-    # given matrix, compute largest differences along any direction
-    winner_dim = [len(mat.shape)]
-    winner_dim.extend(mat.shape)
-    winners = np.zeros(winner_dim)
-
-    # for every dimension (fitting parameter)
-    for i in range(len(mat.shape)):
-        # build delta matrix
-        # certain versions of numpy throw an "invalid value encountered" RuntimeError here but the function behaves correctly
-        with np.errstate(invalid='ignore'):
-            deltas_here = np.absolute(np.diff(mat,axis=i))
-        pad_widths = [(0,0) for j in range(len(mat.shape))]
-        pad_widths[i] = (1,1)
-        deltas_here = np.pad(deltas_here, pad_widths, mode='constant', constant_values=0)
-
-        # build "winner" matrix in this direction (ignore nans)
-        # this is really ugly because we have to index in at variable positions...
-        # likewise here with the error
[…]

### 2018-08-22 bayesim/utils.py

@@ -1,0 +1,55 @@
+from copy import deepcopy
+import numpy as np
+import pandas as pd
+
+def calc_deltas(grp, inds, param_lengths, model_data, fit_param_names, probs, output_var):
+    # construct matrix of output_var({fit_params})
+    subset = deepcopy(model_data.loc[inds])
+    # sort and reset index of subset to match probs so we can use the find_neighbor_boxes function if needed
+    subset.drop_duplicates(subset=fit_param_names, inplace=True)
+    subset.sort_values(fit_param_names, inplace=True)
+    subset.reset_index(inplace=True)
+    if not len(subset.index)==len(probs.points.index):
+        raise ValueError("Subset at EC's %s does not match probability grid!"%str(grp))
+
+    # check if on a grid
+    if not len(subset)==np.product(param_lengths):
+        is_grid = False
+        # construct grid at the highest level of subdivision
+        dense_grid = probs.populate_dense_grid(df=subset, col_to_pull=output_var, make_ind_lists=True)
+        mat = dense_grid['mat']
+        ind_lists = dense_grid['ind_lists']
+
+    else:
+        is_grid = True
+        mat = np.reshape(list(subset[output_var]), param_lengths)
+
+    # given matrix, compute largest differences along any direction
+    winner_dim = [len(mat.shape)]
+    winner_dim.extend(mat.shape)
+    winners = np.zeros(winner_dim)
+
+    # for every dimension (fitting parameter)
+    for i in range(len(mat.shape)):
+        # build delta matrix
+        # certain versions of numpy throw an "invalid value encountered" RuntimeError here but the function behaves correctly
+        with np.errstate(invalid='ignore'):
+            deltas_here = np.absolute(np.diff(mat,axis=i))
+        pad_widths = [(0,0) for j in range(len(mat.shape))]
+        pad_widths[i] = (1,1)
+        deltas_here = np.pad(deltas_here, pad_widths, mode='constant', constant_values=0)
+
+        # build "winner" matrix in this direction (ignore nans)
+        # this is really ugly because we have to index in at variable positions...
+        # likewise here with the error
+        with np.errstate(invalid='ignore'):
[…]

### 2018-08-23 paper/Manuscript.tex
latest paper version

@@
 
-\section*{Model}
-  \todo[inline]{Should this section title actually just be ``Technical Background`` as well perhaps?}
+\section*{Technical Background}
 
@@
   \subsection{Ideal Diode Model}
-    \begin{itemize}
-      \item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters
-      \item figure 3 showing PMF
-    \end{itemize}
+    As a first example, we fit a simple two-parameter model of solar cell current density $J$ (as a function of voltage $V$ and temperature $T$) known as the ideal diode model:
+
+    \begin{equation}
+      J(V,T) = J_L+J_0\left(\exp{\frac{qV}{nkT}}-1\right)
+    \end{equation}
+
+    where $k=8.61733\times 10^{-5}$ eV/K is Boltzmann's constant, by convention $J_L$ (the light current) is negative and $J_0$ (the saturation current) is positive but strongly dependent on temperature, a dependence we can approximate as:
+
+    \begin{equation}
+      J_0 \approx B'T^{3/n}\exp{\left(\frac{-E_{g0}}{nkT}\right)}
+    \end{equation}
+
+    where $E_{g0}$ is the zero-temperature bandgap of the material.
+For this example, we will set this to 1.2 eV and $J_L$ to -0.03 mA/cm$^2$.
+There are thus two parameters to be fit, the coefficient $B'$ (which can range over a wide variety of values) and the ideality factor $n$ (which is by definition between 1 and 2).
+
+    As validation, we generate the ``observations" using the same model we'll use for fitting, with parameter values of $n=1.36$ and $B'=258$, and four temperature values of 150, 200, 250, and 300 K.
 

### 2018-08-27 bayesim/model.py
running in serial on Windows

@@ -11,6 +11,7 @@ import os
 import sys
 from joblib import Parallel, delayed, cpu_count
 import time
+import platform
 
 class Model(object):
     """
@@ -800,8 +801,14 @@ class Model(object):
 
         deltas = np.zeros(len(self.model_data))
 
-        # for every set of conditions...
-        deltas_list = Parallel(n_jobs=cpu_count())(delayed(calc_deltas)(grp, self.model_data_ecgrps.groups[grp], param_lengths, self.model_data, self.fit_param_names(), self.probs, self.output_var) for grp in self.model_data_ecgrps.groups)
+        if platform.system()=='Windows':
+            # need to do it in serial
+            deltas_list = []
+            for grp in self.model_data_ecgrps.groups:
+                deltas_list.append(calc_deltas(grp, self.model_data_ecgrps.groups[grp], param_lengths, self.model_data, self.fit_param_names(), self.probs, self.output_var))
+        else:
+            # parallalize!
+            deltas_list = Parallel(n_jobs=cpu_count())(delayed(calc_deltas)(grp, self.model_data_ecgrps.groups[grp], param_lengths, self.model_data, self.fit_param_names(), self.probs, self.output_var) for grp in self.model_data_ecgrps.groups)
 
         for entry in deltas_list:
             inds = self.model_data_ecgrps.groups[entry[0]]

### 2018-08-28 paper/Manuscript.tex
latest paper stuff, etc.

@@
   \begin{figure}
-    \includegraphics[width=0.7\columnwidth]{structure.png}
-    \caption{\texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces.}
+    \includegraphics[width=0.55\columnwidth]{structure.png}
+    \includegraphics[width=0.4\columnwidth]{flowchart.png}
+    \caption{Left: \texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces.
+Right: Flowchart of use of \texttt{bayesim}.
+(I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}
     \label{structure}
@@
 
-  The structure of \texttt{bayeim} is shown in ~\autoref{structure}. Detailed and up-to-date documentation of classes, functions, and example applications is maintained online.~\cite{docs}
-
-  \subsection{Structure}
-
-    The top-level object with which users interact is implemented in the \texttt{Model} class.
+  The basic structure of \texttt{bayesim} is shown in ~\autoref{structure}a.
+Detailed and up-to-date documentation of classes, functions, and example applications is maintained online.~\cite{docs} The top-level object with which users interact is implemented in the \texttt{Model} class.
 The \texttt{params} module defines classes to store information about the various types of parameters (fitting parameters, experimental conditions, and measured output) while the \texttt{Pmf} class stores the probability distribution and implements the manipulations required for Bayesian updates.
 
-  \subsection{Interfaces}
+  ~\autoref{structure}b is a flowchart of using the code, with the main inference loop surrounded by a dotted line.
+One first needs to provide the observed and modeled data.
+Observed data is accepted in HDF5 format, while modeled data can be an HDF5 file (in which case \texttt{bayesimn} will determine the fitting parameter space grid from this file), or if the fitting parameter space has been predefined, one can also attach a Python function that computes the model data (e.g.
+an interface to a numerical model).
+Observed data should have associated experimental uncertainties, or the user can indicate a fixed value of uncertainty to use for all observations upon attaching the data.
+
+  \todo{do we need a figure for this?} Once modeled data is attached, model uncertainty can be computed.
+At each point in the space of experimental conditions, a matrix of the simulated output variable as a function of the fitting parameters is constructed and at each point in this matrix, the largest difference along any index is computed.
+This is set as the model uncertainty for this set of experimental conditions at this point in parameter space.
+
+  At this point, the inference loop can proceed.
+We start with a bounded prior distribution over the entire parameter space grid and the observed data in a randomized order.
+We feed in one piece of evidence (i.e.
+one observed data point) and compute the likelihood using a Gaussian.
+The standard deviation for each point in the parameter space is the sum of the experimental uncertainy of that observation and the model uncertainty at that point.
+The posterior distribution is computed as a Bayesian update on the prior.
+Next, we check whether the threshold condition for concentration of probability (defined as at least some percentage (by default 90\%) of the probability mass residing in at most some percentage (by default 5\%) of the parameter space volume.
+If this threshold is satisfied, the current posterior is stored and the prior reset to a uniform distribution.
+If not, the next observation is fed in.
+This procedure is repeated until the requisite number (by default, 80\%) of observed data points has been used, with the final posterior being the average of every stored posterior.
+The posterior is calculated in this way (rather than a Bayesian multiplication through every single observed point) to avoid numerical errors that can arise if very small numbers are multiplied together.
+
+  Now the grid can be subdivided.
+The user defines a threshold probability (by default 0.001) for a grid box to possess, and all boxes with greater than this probability, as well as all their immediate neighbors, are divided in two along every parameter.
+\texttt{bayesim} saves a list of the new model calculations that need to be done for inference to proceed again, and the user provides these, again either as a callable or an HDF5 file.
+For the next round of inference, the user can also define a ``bias" parameter from 0 to 0.5 (default 0) that will mix in some fraction of the posterior from the previous step with the uniform distribution over this new grid.
+
+  This overall procedure can be repeated as many times as the user wishes to get a more precise fit -- eventually, the concentration of probability becomes limited by experimental rather than model uncertainty.
+There is also an option to define a minimum width for a box along any parameter direction, and if a box is already less than this width, \texttt{bayesim} will not subdivide in that direction.
+
   The most flexible way to interact with \texttt{bayesim} is via Python scripting or through literate programming in a Jupyter notebook.
@@
 
-  \subsection{Dependencies}
   \texttt{bayesim} relies on a variety of external open-source packages.
@@
       J(V,T) = J_L+J_0\left(\exp{\frac{qV}{nkT}}-1\right)
+      \label{ID_eqn}
     \end{equation}
@@
 
+    \begin{figure}
+      \includegraphics[width=0.45\columnwidth]{diode_obs.png}
+      \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
+      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
+      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
+      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
+      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
+      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
+      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
+      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively.
+``True'' values for the parameters indicated on the PMF in red.
+(this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
+      \label{ID_data}
+    \end{figure}
+
     As validation, we generate the ``observations" using the same model we'll use for fitting, with parameter values of $n=1.36$ and $B'=258$, and four temperature values of 150, 200, 250, and 300 K.
+These ``observations" are shown in ~\autoref{ID_data}a.
+When \texttt{bayesim} imports observed data, it can optionally discard data points that are very close by to each other in order to reduce computational load on modeling less informative points - this capacity is demonsrated in ~\autoref{ID_data}b.
+
+    The next three rows of ~\autoref{ID_data} show the posterior distributions, comparison of JV data between observations and the three highest-probability model points, and absolute errors thereof, on the initial grid and after one and two rounds of subdivision.
+Note that the ranges on the parameter values get narrower as does the scale of absolute errors.
 

### 2018-08-30 paper/Manuscript.tex
cleaning docs, some paper updates

@@
 \begin{abstract}
+  \hl{abstract text here}
+
   Target journal: Computer Physics Communications
@@
    \includegraphics[width=0.7\columnwidth]{figure_1.png}
-   \caption{(Figure copied from docs website for now, will make a publication-appropriate version)}
+   \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
    \label{fig1}
@@
 Right: Flowchart of use of \texttt{bayesim}.
-(I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}
+\hl{(I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}}
     \label{structure}
@@
     \begin{figure}
-      \includegraphics[width=0.45\columnwidth]{diode_obs.png}
+      \includegraphics[width=0.33\columnwidth]{diode_obs.png}
       \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
-      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
-      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
-      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
-      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
-      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
-      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
-      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively.
+%      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
+%      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
+%      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
+%      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
+%      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
+%      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
+%      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively.
 ``True'' values for the parameters indicated on the PMF in red.
 (this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
+      \includegraphics[width=0.8\columnwidth]{all_PMFs.png}
+      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, c) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively.
+Values used to generate data indicated in red.
+\hl{(PMF figure will have a legend and I will add error plots, also observation data could be presented better too)}}
       \label{ID_data}
@@
 
-    The next three rows of ~\autoref{ID_data} show the posterior distributions, comparison of JV data between observations and the three highest-probability model points, and absolute errors thereof, on the initial grid and after one and two rounds of subdivision.
+    %The next three rows of ~\autoref{ID_data} show the posterior distributions, comparison of JV data between observations and the three highest-probability model points, and absolute errors thereof, on the initial grid and after one and two rounds of subdivision.
 Note that the ranges on the parameter values get narrower as does the scale of absolute errors.
 
+    The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating.
+In addition, on the first inference run (prior to any subdivision), an average of 46\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did.
+
   \subsection{SnS Solar Cell}
-    \begin{itemize}
-      \item more practical example - replicating fit from Joule paper
-      \item figure 4 showing PMF and comparison of JV curves
-    \end{itemize}
+    This example aims to demonstrate a more realistic application of \texttt{bayesim}, i.e.
+when the model being used to compute likelihoods is more computationally expensive.
+In this case, we will repeat the analysis from Ref.~\cite{SnSJoule}, using SCAPS~\cite{SCAPS} as the model, which takes 10-15 core-seconds for a single J-V sweep.
+
+    We start on significantly coarser grid than Ref.~\cite{SnSJoule} and will show one level of subdivision.
 

### 2018-08-30 docs/conf.py

@@ -117,9 +117,9 @@ html_static_path = ['_static']
 # default: ``['localtoc.html', 'relations.html', 'sourcelink.html',
 # 'searchbox.html']``.
 #
-html_sidebars = {
-    'sidebar': ['localtoc.html', 'sourcelink.html', 'searchbox.html']
-}
+#html_sidebars = {
+#    'sidebar': ['localtoc.html', 'sourcelink.html', 'searchbox.html']
+#}
 
 # -- Options for HTMLHelp output ---------------------------------------------
 

### 2018-08-31 paper/Manuscript.tex
working on plotting and paper

@@
  \begin{figure}
-   \includegraphics[width=0.7\columnwidth]{figure_1.png}
+   \includegraphics[width=0.9\columnwidth]{figure_1.png}
    \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
@@
   \begin{figure}
-    \includegraphics[width=0.55\columnwidth]{structure.png}
-    \includegraphics[width=0.4\columnwidth]{flowchart.png}
-    \caption{Left: \texttt{bayesim} software structure, indicating class definitions, internal and external dependencies, and interfaces.
-Right: Flowchart of use of \texttt{bayesim}.
-\hl{(I will update these to make a more sensible figure with less white space, and also add subdivision into the loop)}}
+    \includegraphics[width=0.25\columnwidth]{structure.png}
+    \includegraphics[width=0.65\columnwidth]{flowchart.png}
+    \caption{Left: \texttt{bayesim} software structure. Right: Flowchart of use of \texttt{bayesim}.}
     \label{structure}
@@
 (this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
-      \includegraphics[width=0.8\columnwidth]{all_PMFs.png}
+      \includegraphics[width=0.8\columnwidth]{diode_pmf_comp.png}
       \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, c) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively.
-Values used to generate data indicated in red.
-\hl{(PMF figure will have a legend and I will add error plots, also observation data could be presented better too)}}
+Values used to generate data indicated in red.}
       \label{ID_data}
@@
     The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating.
-In addition, on the first inference run (prior to any subdivision), an average of 46\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did.
+In addition, on the first inference run (prior to any subdivision), an average of 43\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did, while the average absolute error of the highest-probability model decreased from 0.03 after the first run to 0.007 after the second subdivision.
 
@@
 
-    We start on significantly coarser grid than Ref.~\cite{SnSJoule} and will show one level of subdivision.
+    \begin{figure}
+      \includegraphics[width=0.7\columnwidth]{SnS_final_pmf.png}
+      \includegraphics[width=0.8\columnwidth]{SnS_probs_Joule}
+      \caption{Above: PMF produced by \texttt{bayesim}.
+Below: PMF from Reference~\cite{SnSJoule}.
+\hl{TBD if we'll actually reproduce the plot from the Joule paper directly vs.
+replotting the data somehow}}
+      \label{SnS_data}
+    \end{figure}
+
+    We start on a significantly coarser grid than Ref.~\cite{SnSJoule} and show only one level of subdivision to make the example feasible to run on a personal computer.
+\~autoref{SnS_data} shows the results from this fit done in \texttt{bayesim} compared to the higher-resolution grid analysis done previously.
+Note that the inference step in full-resolution grid took a few hours, while the adaptive grid fit takes a few minutes.
+While the fit precision is of course lower at only one level of subdivision, the extracted values are generally in agreement and more importantly, the relationship between the mobility and lifetime (namely, that the product, i.e.
+the diffusion length), is constrained, emerges just as clearly.
 

### 2018-08-31 bayesim/model.py

@@ -489,6 +489,7 @@ class Model(object):
             num_ecs (`int`): number of EC values to plot, defaults to 1 (ignored if ecs is provided)
             num_param_pts (`int`): number of the most probable parameter space points to plot (defaults to 1)
             ec_x_var (`str`): one of self.ec_names, will overwrite if this was provided before in attach_observations, required if it wasn't. If ec was provided, this will supercede that
+            return_avg_err (bool): whether or not to return average (absolute) error for highest probability model over all EC's plotted (defaults to False)
             fpath (`str`): optional, path to save image to if desired
         """
         if 'ec_x_var' in argv.keys():
@@ -497,6 +498,9 @@ class Model(object):
         if self.params.ec_x_name==None:
             print('You have not provided an x-variable from your experimental conditions against which to plot. Choosing the first one in the list, %s.\n'%(self.ec_names()[0]))
             self.params.set_ec_x(self.ec_names()[0])
+
+        return_avg_err = argv.get('return_avg_err', False)
+        all_errs = []
 
         other_ecs = [c for c in self.params.ecs if not c.name==self.params.ec_x_name]
         #print(self.params.ec_x_name, [c.name for c in other_ecs])
@@ -567,6 +571,9 @@ class Model(object):
                         model_data =  model_data[abs(model_data[c.name]-ecs_here[c.name])<=10.**(-1.*c.tol_digits)]
                 model_data.sort_values(by=[self.params.ec_x_name])
                 errors = np.subtract(model_data[self.output_var], obs_data[self.output_var])
+                if c_ind==1: #take errors from highest probability
+                    all_errs.extend([abs(e) for e in errors])
+
                 axs[i,0].plot(model_data[self.params.ec_x_name], model_data[self.output_var], color=color)
                 axs[i,1].plot(model_data[self.params.ec_x_name], errors, color=color)
                 leg_label = 'modeled: '
@@ -603,6 +610,9 @@ class Model(object):
         plt.tight_layout()
         if 'fpath' in argv.keys():
             plt.savefig(argv['fpath'])
+
+        if return_avg_err:
+            return np.mean(all_errs)
 
     def run(self, **argv):
         """

### 2018-08-31 bayesim/overlaid_pmf.py

@@ -1,0 +1,65 @@
+m1 = bym.Model(load_state=True, state_file='after_run_1.h5')
+m2 = bym.Model(load_state=True, state_file='after_run_2.h5')
+m3 = bym.Model(load_state=True, state_file='after_run_3.h5')
+
+m1_n_bins, m1_n_probs = m1.probs.project_1D(m1.params.fit_params[1])
+m2_n_bins, m2_n_probs = m2.probs.project_1D(m2.params.fit_params[1])
+m3_n_bins, m3_n_probs = m3.probs.project_1D(m3.params.fit_params[1])
+
+m1_Bp_bins, m1_Bp_probs = m1.probs.project_1D(m1.params.fit_params[0])
+m2_Bp_bins, m2_Bp_probs = m2.probs.project_1D(m2.params.fit_params[0])
+m3_Bp_bins, m3_Bp_probs = m3.probs.project_1D(m3.params.fit_params[0])
+
+m1_patches = m1.probs.project_2D(m1.params.fit_params[0], m1.params.fit_params[1])
+m2_patches = m2.probs.project_2D(m2.params.fit_params[0], m2.params.fit_params[1])
+m3_patches = m3.probs.project_2D(m3.params.fit_params[0], m3.params.fit_params[1])
+
+import matplotlib.patches as mplp
+
+prop_cycle = plt.rcParams['axes.prop_cycle']
+colors = prop_cycle.by_key()['color']
+
+fig, axes = plt.subplots(nrows=2, ncols=2, figsize=(10,10))
+
+fs=20
+
+for rownum in [0,1]:
+    for colnum in [0,1]:
+        for item in ([axes[rownum][colnum].xaxis.label, axes[rownum][colnum].yaxis.label] +axes[rownum][colnum].get_xticklabels() + axes[rownum][colnum].get_yticklabels()):
+                    item.set_fontsize(fs)
+
+axes[0,0].hist(m1.params.fit_params[0].vals, weights=m1_Bp_probs, bins=m1_Bp_bins)
+axes[0,0].hist(m2.params.fit_params[0].vals, weights=m2_Bp_probs, bins=m2_Bp_bins)
+axes[0,0].hist(m3.params.fit_params[0].vals, weights=m3_Bp_probs, bins=m3_Bp_bins)
+axes[0,0].set_xscale('log')
[…]

### 2018-08-31 bayesim/pmf.py

@@ -584,10 +584,15 @@ class Pmf(object):
             just_grid (`bool`): whether to show only the grid (i.e. visualize subdivisions) or the whole PMF (defaults to False)
             fpath (`str`): optional, path to save image to
             true_vals (`dict`): optional, set of param values to highlight on PMF
+            return_plots (bool): whether to return figure and axes (used by visualize_PMF_sequence in utils), default False
         """
         # read in options
         frac_points = argv.get('frac_points', 1.0)
         just_grid = argv.get('just_grid', False)
+        return_plots = argv.get('return_plots', False)
+        if return_plots:
+            plt.ioff()
+
         if 'fpath' in argv.keys():
             fpath = argv['fpath']
 
@@ -661,6 +666,9 @@ class Pmf(object):
                         # formatting
                         axes[rownum][colnum].set_ylim(0,1)
                         axes[rownum][colnum].yaxis.set_label_position("right")
+                        axes[rownum][colnum].yaxis.tick_right()
+                        for label in axes[rownum][colnum].get_yticklabels():
+                            label.set_fontsize(20)
                         axes[rownum][colnum].set_ylabel('P(%s)'%x_param.display_name, rotation=270, labelpad=20) #labelpad is kind of a brute-force way to do this and might break if we change the figure size, but va='bottom' wasn't working
                         #axes[rownum][colnum].`grid`(axis='y')
 
@@ -717,3 +725,10 @@ class Pmf(object):
 
         if 'fpath' in argv.keys():
             plt.savefig(fpath)
+
+        if return_plots:
+            return fig, axes
+            plt.close()
+
+        else:
+            plt.show()

### 2018-08-31 bayesim/utils.py

@@ -1,6 +1,118 @@
 from copy import deepcopy
 import numpy as np
 import pandas as pd
+import sys
+import bayesim.params as pm
+#import bayesim.model as bym
+import model as bym
+import bayesim.pmf as pmf
+import matplotlib.pyplot as plt
+import matplotlib.patches as mplp
+from matplotlib import colors as mcolors
+
+def visualize_PMF_sequence(statefile_list, **argv):
+    """
+    Create plot akin to that produced by pmf.visualize() but with data from multiple PMF's overlaid. All should have the same set of fitting parameters. For now assumes that first statefile has the largest axes bounds, will add automated check later.
+
+    Args:
+        statefile_list (list of str): list of paths to statefiles (saved by Model.save_state function storing PMF's to be visualized), in order from least to most subdivided
+        name_list (list of str): optional, list of names for legend, defaults to filenames
+        true_vals (`dict`): optional, set of param values to highlight on PMF
+        fpath (str): optional, path to save image to
+    """
+
+    # get legend names
+    if 'name_list' in argv.keys():
+        name_list = argv['name_list']
+    else:
+        name_list = [sf.split('/')[-1].split('.')[0] for sf in statefile_list]
+
+    if 'true_vals' in argv.keys():
+        plot_true_vals = True
+        true_vals = argv['true_vals']
+    else:
+        plot_true_vals = False
+
+    # load the models one by one (to save RAM) and get visualizations
+    figs = []
+    axes_sets = []
+    for statefile in statefile_list:
+        m = bym.Model(load_state=True, state_file=statefile)
+        if plot_true_vals:
+            f, a = m.probs.visualize(return_plots=True, true_vals=true_vals)
+        else:
+            f, a = m.probs.visualize(return_plots=True)
+        figs.append(f)
+        axes_sets.append(a)
+    num_params = len(m.params.fit_params)
+
+    # get color cycle
+    prop_cycle = plt.rcParams['axes.prop_cycle']
+    colors = prop_cycle.by_key()['color']
+
+    # initialize the figure
+    fig, axes = plt.subplots(nrows=num_params, ncols=num_params, figsize=(5*num_params, 5*num_params))
+
+    for rownum in range(num_params):
+        for colnum in range(num_params):
+            for i in range(len(figs)):
+                old_ax = axes_sets[i][rownum][colnum]
+                color = colors[i]
+                patches = old_ax.patches
+                if i==0: # formatting stuff
[…]

### 2018-09-04 paper/Manuscript.tex
first full draft of main text of paper, some figure work still to do plus abstract and appendix

@@
     We start on a significantly coarser grid than Ref.~\cite{SnSJoule} and show only one level of subdivision to make the example feasible to run on a personal computer.
-\~autoref{SnS_data} shows the results from this fit done in \texttt{bayesim} compared to the higher-resolution grid analysis done previously.
+~\autoref{SnS_data} shows the results from this fit done in \texttt{bayesim} compared to the higher-resolution grid analysis done previously.
 Note that the inference step in full-resolution grid took a few hours, while the adaptive grid fit takes a few minutes.
@@
 \section*{Conclusions}
- talk about broader applicability of approach
+ We have introduced \texttt{bayesim}, a Python-based adaptive grid sampled Bayesian inference code which is flexible to the model used to calculated likelihood as well as the parameter space over which to fit.
+We provided two examples of application of the code in the space of characterizing PV devices using JVT(i) measurements, as this is the authors' area of expertise.
+However, nothing about the code or the approach limits it to application in PV materials.
+Any situation where there is:
+ \begin{itemize}
+   \item a forward model that captures the relevant physics (particularly one that is relatively expensive to evaluate), and
+   \item a set of measurements of the output of that model as a function of several experimental conditions
+ \end{itemize}
+ would be amenable to \texttt{bayesim}.
+The online documentation page~\cite{docs} maintains a list of examples which will grow as the authors become aware of/implement more.
+This website also hosts other useful information, such as detailed documentation of every class and function in \texttt{bayesim}, a more extensive technical background section than is included here, and an updated manual for usage of the code.
 
 \section*{Acknowledgements}
+R.C.K.
+acknowledges the funding of a Blue Waters Graduate Fellowship.
+The SnS work referenced in~\cite{SnSJoule} was funded by a Google Faculty Research Award, as well as the Center for Next Generation Materials by Design (CNGMD), an Energy Frontier Research Center funded by the U.S.
+Department of Energy, Office of Science, Basic Energy Sciences.
 
@@
  \begin{itemize}
-   \item include minimal code to run ideal diode example
+   \item include minimal code to run ideal diode example via CLI
    \item link to Github repo (which has installation instructions and documentation as well as list of planned future features)

### 2018-09-04 paper/Manuscript.tex
updating figures

@@
    \includegraphics[width=0.9\columnwidth]{figure_1.png}
-   \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
+   \caption{a) High-level flowchart of inputs and outputs to \texttt{bayesim}, b) 2D schematic of adaptive grid sampling approach.}
    \label{fig1}
@@
   \begin{figure}
-    \includegraphics[width=0.25\columnwidth]{structure.png}
-    \includegraphics[width=0.65\columnwidth]{flowchart.png}
-    \caption{Left: \texttt{bayesim} software structure. Right: Flowchart of use of \texttt{bayesim}.}
+    %\includegraphics[width=0.25\columnwidth]{structure.png}
+    %\includegraphics[width=0.65\columnwidth]{flowchart.png}
+    \includegraphics[width=0.95\columnwidth]{figure_2.png}
+    \caption{a) \texttt{bayesim} software structure. b) Detailed flowchart of use of \texttt{bayesim}, with calculation steps and various levels of iteration indicated.}
     \label{structure}
@@
 
-  At this point, the inference loop can proceed.
+  At this point, the Bayesian inference loop can proceed.
 We start with a bounded prior distribution over the entire parameter space grid and the observed data in a randomized order.
@@
 The posterior is calculated in this way (rather than a Bayesian multiplication through every single observed point) to avoid numerical errors that can arise if very small numbers are multiplied together.
+This procedure of running the Bayesian loop multiple times until the desired number of pieces of evidence are used is encapsulated in the \texttt{Model.run()} function.
 

### 2018-09-05 bayesim/model.py
forgot to stage a few other things

@@ -175,13 +175,13 @@ class Model(object):
             keep_all (`bool`): whether to keep all the data in the file (longer simulation times) or to clip out data points that are close to each other (defaults to False)
             ec_x_var (`str`): required if keep_all is False, the experimental condition over which to measure differences (e.g. V for JV(Ti) curves in PV). It will also be used in plotting later.
             max_ec_x_step (`float`): used if keep_all is False, largest step to take in the ec_x_var before keeping a point even if curve if "flat" (defaults to 0.05 * range of ec_x_var)
-            thresh_dif_frac (`float`): used if keep_all is False, threshold (as a percentage of the maximum value, defaults to 0.03)
+            thresh_dif_frac (`float`): used if keep_all is False, threshold (as a percentage of the range of values, defaults to 0.01)
             fixed_unc (`float`): required if running in function mode or if file doesn't have an 'uncertainty' column, value to use as uncertainty in measurement
             output_column (`str`): optional, header of column containing output data (required if different from self.output_var)
             verbose (`bool`): flag for verbosity, defaults to False
         """
         output_col = argv.get('output_column', self.output_var)
-        keep_all = argv.get('keep_all', True)
+        keep_all = argv.get('keep_all', False)
         thresh_dif_frac = argv.get('thresh_dif_frac', 0.01)
         verbose = argv.get('verbose', False)
 

### 2018-09-05 bayesim/overlaid_pmf.py
oops still hadn't staged everything

@@ -1,65 +1,0 @@
-m1 = bym.Model(load_state=True, state_file='after_run_1.h5')
-m2 = bym.Model(load_state=True, state_file='after_run_2.h5')
-m3 = bym.Model(load_state=True, state_file='after_run_3.h5')
-
-m1_n_bins, m1_n_probs = m1.probs.project_1D(m1.params.fit_params[1])
-m2_n_bins, m2_n_probs = m2.probs.project_1D(m2.params.fit_params[1])
-m3_n_bins, m3_n_probs = m3.probs.project_1D(m3.params.fit_params[1])
-
-m1_Bp_bins, m1_Bp_probs = m1.probs.project_1D(m1.params.fit_params[0])
-m2_Bp_bins, m2_Bp_probs = m2.probs.project_1D(m2.params.fit_params[0])
-m3_Bp_bins, m3_Bp_probs = m3.probs.project_1D(m3.params.fit_params[0])
-
-m1_patches = m1.probs.project_2D(m1.params.fit_params[0], m1.params.fit_params[1])
-m2_patches = m2.probs.project_2D(m2.params.fit_params[0], m2.params.fit_params[1])
-m3_patches = m3.probs.project_2D(m3.params.fit_params[0], m3.params.fit_params[1])
-
-import matplotlib.patches as mplp
-
-prop_cycle = plt.rcParams['axes.prop_cycle']
-colors = prop_cycle.by_key()['color']
-
-fig, axes = plt.subplots(nrows=2, ncols=2, figsize=(10,10))
-
-fs=20
-
-for rownum in [0,1]:
-    for colnum in [0,1]:
-        for item in ([axes[rownum][colnum].xaxis.label, axes[rownum][colnum].yaxis.label] +axes[rownum][colnum].get_xticklabels() + axes[rownum][colnum].get_yticklabels()):
-                    item.set_fontsize(fs)
-
-axes[0,0].hist(m1.params.fit_params[0].vals, weights=m1_Bp_probs, bins=m1_Bp_bins)
-axes[0,0].hist(m2.params.fit_params[0].vals, weights=m2_Bp_probs, bins=m2_Bp_bins)
-axes[0,0].hist(m3.params.fit_params[0].vals, weights=m3_Bp_probs, bins=m3_Bp_bins)
-axes[0,0].set_xscale('log')
[…]

### 2018-09-05 setup.py

@@ -3,7 +3,7 @@ import os
 
 
 setup(name='bayesim',
-      version='0.9.01',
+      version='0.9.4',
       description='Fast model fitting via Bayesian inference',
       author='Rachel Kurchin, Giuseppe Romano',
       author_email='rkurchin@mit.edu, romanog@mit.edu',

### 2018-09-06 paper/Manuscript.tex
latest paper version

@@
 \raggedbottom\usepackage[bottom]{footmisc} \makeatletter \def\p@section{} \def\p@subsubsection{} \makeatother\begin{document}
-\title{\texttt{bayesim}: a tool for fast model fitting with Bayesian inference}
+
+\title{Bayesim: a tool for adaptive grid model fitting with Bayesian inference}
+
 \author{Rachel Kurchin}
@@
 
+ i.e.
+as each new piece of evidence is fed in, the posterior probability distribution is updated to accommodate it and should in general become more concentrated into one region of parameter space.
 In a multidimensional parameter estimation problem, each hypothesis $H$ is a tuple of possible values for the fitting parameters, i.e.
@@
     \includegraphics[width=0.95\columnwidth]{figure_2.png}
-    \caption{a) \texttt{bayesim} software structure. b) Detailed flowchart of use of \texttt{bayesim}, with calculation steps and various levels of iteration indicated.}
+    \caption{a) \texttt{bayesim} software structure.
+b) Detailed flowchart of use of \texttt{bayesim}, with calculation steps and various levels of iteration indicated.
+Boxes in blue indicate steps that can or must be done explicitly by the user, grey steps that are done by the code with behavior tunable by the user, orange diamonds control points for staying in or leaving a loop, and green the final output.}
     \label{structure}
@@
 
-  \todo{do we need a figure for this?} Once modeled data is attached, model uncertainty can be computed.
+  Once modeled data is attached, model uncertainty can be computed.
 At each point in the space of experimental conditions, a matrix of the simulated output variable as a function of the fitting parameters is constructed and at each point in this matrix, the largest difference along any index is computed.
@@
   At this point, the Bayesian inference loop can proceed.
-We start with a bounded prior distribution over the entire parameter space grid and the observed data in a randomized order.
+We start with a bounded uniform prior distribution over the entire parameter space grid and the observed data in a randomized order.
 We feed in one piece of evidence (i.e.
@@
 \texttt{bayesim} saves a list of the new model calculations that need to be done for inference to proceed again, and the user provides these, again either as a callable or an HDF5 file.
-For the next round of inference, the user can also define a ``bias" parameter from 0 to 0.5 (default 0) that will mix in some fraction of the posterior from the previous step with the uniform distribution over this new grid.
+For the next round of inference, the user can also define a ``relaxation" parameter from 0 to 1.0 (default 0) that will mix in some fraction of the posterior from the previous step with the uniform distribution over this new grid.
 
@@
     \begin{figure}
-      \includegraphics[width=0.33\columnwidth]{diode_obs.png}
-      \includegraphics[width=0.45\columnwidth]{diode_obs_zoom.png}
-%      \includegraphics[width=0.3\columnwidth]{diode_pmf_1.png}
-%      \includegraphics[width=0.65\columnwidth]{diode_comp_1.png}
-%      \includegraphics[width=0.3\columnwidth]{diode_pmf_2.png}
-%      \includegraphics[width=0.65\columnwidth]{diode_comp_2.png}
-%      \includegraphics[width=0.3\columnwidth]{diode_pmf_3.png}
-%      \includegraphics[width=0.65\columnwidth]{diode_comp_3.png}
-%      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, Next three rows: PMF's, comparisons of highest three probability model points with observed data, and absolute errors thereof, on the initial grid, and after one and two subdivisions, respectively.
-``True'' values for the parameters indicated on the PMF in red.
-(this figure is a giant data dump right now; I'm figuring out how to make it less terrifyingly overwhelming - like possibly overlaying all three PMF's onto one plot in different colors)}
-      \includegraphics[width=0.8\columnwidth]{diode_pmf_comp.png}
-      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, b) Observed data saved by \texttt{bayesim}, with zoom to show where neglected data points were, c) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively.
+      \includegraphics[width=0.8\columnwidth]{figure_3.png}
+      \caption{a) ``Observations" generated by ideal diode model, Equation~\ref{ID_eqn}, with overlaid scatter to show which points were actually imported and used by \texttt{bayesim}, b) PMF's after the first inference run, second (one subdivision), and third (two subdivision), in blue, orange, and green, respectively.
 Values used to generate data indicated in red.}
@@
 These ``observations" are shown in ~\autoref{ID_data}a.
-When \texttt{bayesim} imports observed data, it can optionally discard data points that are very close by to each other in order to reduce computational load on modeling less informative points - this capacity is demonsrated in ~\autoref{ID_data}b.
-
-    %The next three rows of ~\autoref{ID_data} show the posterior distributions, comparison of JV data between observations and the three highest-probability model points, and absolute errors thereof, on the initial grid and after one and two rounds of subdivision.
-Note that the ranges on the parameter values get narrower as does the scale of absolute errors.
+When \texttt{bayesim} imports observed data, it can optionally discard data points that are very close by to each other in order to reduce computational load on modeling less informative points -- the observed points that were actually imported (59 out of 305 total ``observations") are shown as overlaid scatter dots.
 
@@
 when the model being used to compute likelihoods is more computationally expensive.
-In this case, we will repeat the analysis from Ref.~\cite{SnSJoule}, using SCAPS~\cite{SCAPS} as the model, which takes 10-15 core-seconds for a single J-V sweep.
+In this case, we will repeat the analysis from Ref.~\cite{SnSJoule}, using SCAPS~\cite{SCAPS} (a coupled drift-diffusion/Poisson solver) as the model, which takes 10-15 core-seconds for a single J-V sweep.
 
     \begin{figure}
-      \includegraphics[width=0.7\columnwidth]{SnS_final_pmf.png}
-      \includegraphics[width=0.8\columnwidth]{SnS_probs_Joule}
-      \caption{Above: PMF produced by \texttt{bayesim}.
-Below: PMF from Reference~\cite{SnSJoule}.
+      \includegraphics[width=0.8\columnwidth]{figure_4.png}
+      \caption{a) PMFs produced by \texttt{bayesim}, after initial run and after one subdivision.
+Inset: device structure (illuminated from above) with bulk SnS ($\mu$,$\tau$ fit) and SnS/Zn(O,S) interface ($\Delta E_\text{c}$, $S_{\text{eff}}$ fit) indicated.
+b) PMF from Reference~\cite{SnSJoule}.
 \hl{TBD if we'll actually reproduce the plot from the Joule paper directly vs.

### 2018-09-06 bayesim/model.py

@@ -624,7 +624,7 @@ class Model(object):
             th_pm (`float`): threshold quantity of probability mass to be concentrated in th_pv fraction of parameter space to trigger the run to stop (defaults to 0.9)
             th_pv (`float`): threshold fraction of parameter space volume for th_pm fraction of probability to be concentrated into to trigger the run to stop (defaults to 0.05)
             min_num_pts (`int`): minimum number of observation points to use - if threshold is reached before this number of points has been used, it will start over and the final PMF will be the average of the number of runs needed to use sufficient points (defaults to 0.7 * the number of experimental measurements)
-            prob_bias (`float`): number from 0 to 0.5, fraction of PMF from previous step to mix into prior for this step (defaults to 0) - higher values will likely converge faster but possibly have larger errors, especially if min_num_pts is small
+            prob_relax (`float`): number from 0 to 1.0, fraction of PMF from previous step to mix into prior for this step (defaults to 0) - higher values will likely converge faster but possibly have larger errors, especially if min_num_pts is small
             verbose (`bool`): flag for verbosity, defaults to False
         """
         # read in options
@@ -633,10 +633,10 @@ class Model(object):
         th_pv = argv.get('th_pv', 0.05)
         min_num_pts = argv.get('min_num_pts', int(0.7*len(self.obs_data)))
         verbose = argv.get('verbose', False)
-        bias = argv.get('prob_bias', 0.0)
-        if bias < 0 or bias > 0.5:
-            print("Bias parameter must be between 0 and 0.5 - defaulting to 0.")
-            bias = 0
+        rel = argv.get('prob_relax', 0.0)
+        if rel < 0 or rel > 1.0:
+            print("Relaxation parameter must be between 0 and 1.0 - defaulting to 0.")
+            rel = 0
         if verbose:
             print('Running inference!\n')
 
@@ -666,7 +666,7 @@ class Model(object):
         uni_probs = deepcopy(self.probs)
         uni_probs.uniformize()
         start_probs = deepcopy(self.probs)
-        start_probs.points['prob'] = bias*old_probs.points['prob'] + (1-bias)*uni_probs.points['prob']
+        start_probs.points['prob'] = rel*old_probs.points['prob'] + (1-rel)*uni_probs.points['prob']
         start_probs.normalize()
 
         # randomize observation order

### 2018-09-06 bayesim/utils.py
trying to fix Binder issue

@@ -3,8 +3,8 @@ import numpy as np
 import pandas as pd
 import sys
 import bayesim.params as pm
-#import bayesim.model as bym
-import model as bym
+import bayesim.model as bym
+#import model as bym
 import bayesim.pmf as pmf
 import matplotlib.pyplot as plt
 import matplotlib.patches as mplp

### 2018-09-06 bayesim/model.py
Binder was still broken, trying again

@@ -1,3 +1,4 @@
+sys.path.append('../../')
 from bayesim.pmf import Pmf
 import bayesim.params as pm
 from bayesim.utils import calc_deltas

### 2018-09-06 bayesim/utils.py

@@ -2,6 +2,7 @@ from copy import deepcopy
 import numpy as np
 import pandas as pd
 import sys
+sys.path.append('../../')
 import bayesim.params as pm
 import bayesim.model as bym
 #import model as bym

### 2018-09-06 bayesim/model.py
fixing Binder, take 3

@@ -1,3 +1,4 @@
+import sys
 sys.path.append('../../')
 from bayesim.pmf import Pmf
 import bayesim.params as pm
@@ -9,7 +10,6 @@ import numpy as np
 import matplotlib.pyplot as plt
 import random
 import os
-import sys
 from joblib import Parallel, delayed, cpu_count
 import time
 import platform

### 2018-09-06 bayesim/model.py
okay maybe Binder is fixed NOW

@@ -1,5 +1,3 @@
-import sys
-sys.path.append('../../')
 from bayesim.pmf import Pmf
 import bayesim.params as pm
 from bayesim.utils import calc_deltas

### 2018-09-06 bayesim/utils.py

@@ -4,8 +4,8 @@ import pandas as pd
 import sys
 sys.path.append('../../')
 import bayesim.params as pm
-import bayesim.model as bym
-#import model as bym
+#import bayesim.model as bym
+import model as bym
 import bayesim.pmf as pmf
 import matplotlib.pyplot as plt
 import matplotlib.patches as mplp

### 2018-09-06 bayesim/utils.py
fifth time's the charm, surely

@@ -2,11 +2,11 @@ from copy import deepcopy
 import numpy as np
 import pandas as pd
 import sys
-sys.path.append('../../')
-import bayesim.params as pm
+#sys.path.append('../../')
+#import bayesim.params as pm
 #import bayesim.model as bym
-import model as bym
-import bayesim.pmf as pmf
+#import model as bym
+#import bayesim.pmf as pmf
 import matplotlib.pyplot as plt
 import matplotlib.patches as mplp
 from matplotlib import colors as mcolors

### 2018-09-06 paper/Manuscript.tex
latest version of paper

@@
 \begin{abstract}
-  \hl{abstract text here}
+  Bayesian inference is a widely used and powerful analytical technique in fields such as astronomy and particle physics but has historically been underutilized in some other disciplines including semiconductor devices.
+In this work, we introduce \texttt{bayesim}, a Python package that utilizes adaptive grid sampling to efficiently generate a probability distribution over multiple input parameters to a forward model using a collection of experimental measurements.
+We discuss the implementation choices made in the code, showcase two examples in photovoltaics, and discuss general prerequisites for the approach to apply to other systems.
 
-  Target journal: Computer Physics Communications
+  [Target journal: Computer Physics Communications]
 \end{abstract}

### 2018-09-07 paper/Manuscript.tex
new paper draft

@@
   The most flexible way to interact with \texttt{bayesim} is via Python scripting or through literate programming in a Jupyter notebook.
-There is also a command line interface (CLI) for users less familiar with coding in Python.
+There is also a command line interface (CLI) for users less familiar with coding in Python planned for future release.
 
@@
       \includegraphics[width=0.8\columnwidth]{figure_4.png}
-      \caption{a) PMFs produced by \texttt{bayesim}, after initial run and after one subdivision.
-Inset: device structure (illuminated from above) with bulk SnS ($\mu$,$\tau$ fit) and SnS/Zn(O,S) interface ($\Delta E_\text{c}$, $S_{\text{eff}}$ fit) indicated.
-b) PMF from Reference~\cite{SnSJoule}.
-\hl{TBD if we'll actually reproduce the plot from the Joule paper directly vs.
-replotting the data somehow}}
+      \caption{PMFs produced by \texttt{bayesim}, after initial run and after one subdivision (Blue and green, respectively).
+In red, PMF from Reference~\cite{SnSJoule}.
+Inset: device structure (illuminated from above) with bulk SnS ($\mu$,$\tau$ fit) and SnS/Zn(O,S) interface ($\Delta E_\text{c}$, $S_{\text{eff}}$ fit) indicated.}
       \label{SnS_data}
@@
     We start on a significantly coarser grid than Ref.~\cite{SnSJoule} and show only one level of subdivision to make the example feasible to run on a personal computer.
-~\autoref{SnS_data} shows the results from this fit done in \texttt{bayesim} compared to the higher-resolution grid analysis done previously.
+\autoref{SnS_data} shows the results from this fit done in \texttt{bayesim} compared to the higher-resolution grid analysis done previously.
 Note that the inference step in full-resolution grid took a few hours, while the adaptive grid fit takes a few minutes.
@@
  would be amenable to \texttt{bayesim}.
-The online documentation page~\cite{docs} maintains a list of examples which will grow as the authors become aware of/implement more.
-This website also hosts other useful information, such as detailed documentation of every class and function in \texttt{bayesim}, a more extensive technical background section than is included here, and an updated manual for usage of the code.
+The online documentation page~\cite{docs} maintains a list of examples which will grow as the authors become aware of/implement more, and the latest version of the code can always be found in the Github repository~\cite{gh}.
+The online documentation also hosts other useful information, such as detailed documentation of every class and function in \texttt{bayesim}, a more extensive technical background section than is included here, and an updated manual for usage of the code.
 
@@
 
-\section*{Appendix}
- \begin{itemize}
-   \item include minimal code to run ideal diode example via CLI
-   \item link to Github repo (which has installation instructions and documentation as well as list of planned future features)
-  \end{itemize}
-
 \bibliography{biblio}

### 2018-09-07 paper/Manuscript.tex
minor manuscript updates

@@
    \includegraphics[width=0.9\columnwidth]{figure_1.png}
-   \caption{a) High-level flowchart of inputs and outputs to \texttt{bayesim}, b) 2D schematic of adaptive grid sampling approach.}
+   \caption{a) High-level flowchart of inputs and outputs to \texttt{bayesim}.
+Observed data as a function of experimental conditions and modeled data over those same conditions as well as fitting parameters are fed in, and the code produces a probability distribution over the fitting parameter values.
+b) 2D schematic of adaptive grid sampling approach, illustrating progressive subdivision in higher-probability regions of parameter space.}
    \label{fig1}

### 2018-09-10 paper/Manuscript.tex
paper updates

@@
 \author{Rachel Kurchin}
-\affiliation{Department of Materials Science \& Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\email{rachel.kurchin@gmail.com}
+\affiliation{Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
 \author{Giuseppe Romano}
-\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\affiliation{Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
 \author{Tonio Buonassisi}
 \email{buonassi@mit.edu}
-\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
+\affiliation{Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
 
@@
 In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters.
-Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.
+Bayesian inference, or Bayesian parameter estimation (BPE) is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.
+It has been widely used for decades in fields such as cosmology~\cite{cosmobayesreview}, particle physics~\cite{particlebayes, higgsbayes}, and biology~\cite{evobiobayes, sysbiobayes}, with well-developed and widely used code packages specialized to these purposes.~\cite{multinest, biobayescode} However, the use of Bayesian inference in materials science and related contexts is much more recent, having only emerged in the past few years.~\cite{lookman, combo, SnSJoule}
 
-  We have previously demonstrated the value of a Bayesian approach in using automated high-throughput temperature- and illumination-dependent current-voltage measurements (JVTi) to fit material/interface properties and defect recombination parameters in photovoltaic (PV) absorbers~\cite{SnSJoule,FeBayes}.
+  We have previously demonstrated the value of a BPE approach in using automated high-throughput temperature- and illumination-dependent current-voltage measurements ($JVTi$) to fit material/interface properties and defect recombination parameters in photovoltaic (PV) absorbers~\cite{SnSJoule,FeBayes}, i.e.
+as a replacement for direct experimental characterization via probabilitistic inversion of a forward model.
 In cases such as these, when the data model is not a simple analytical equation but rather a computationally intensive numerical model, efficient, nonredundant sampling of the parameter space when computing likelihoods becomes critical to making the fit feasible.
 
-  In this work, we introduce \texttt{bayesim}, a Python-based code that utilizes adaptive grid sampling to perform Bayesian parameter estimation.
+  In this work, we introduce \texttt{bayesim}, a Python-based code that utilizes adaptive grid sampling to perform BPE.
+It is designed to be easy to use by anyone with basic familiarity with Python.
 We discuss the structure of the code, its implementation, and provide several examples of its usage.
@@
 One first needs to provide the observed and modeled data.
-Observed data is accepted in HDF5 format, while modeled data can be an HDF5 file (in which case \texttt{bayesimn} will determine the fitting parameter space grid from this file), or if the fitting parameter space has been predefined, one can also attach a Python function that computes the model data (e.g.
+Observed data is accepted in HDF5 format, while modeled data can be an HDF5 file (in which case \texttt{bayesim} will determine the fitting parameter space grid from this file), or if the fitting parameter space has been predefined, one can also attach a Python function that computes the model data (e.g.
 an interface to a numerical model).
@@
     The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating.
-In addition, on the first inference run (prior to any subdivision), an average of 43\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 2\% did, while the average absolute error of the highest-probability model decreased from 0.03 after the first run to 0.007 after the second subdivision.
+In addition, on the first inference run (prior to any subdivision), an average of 45\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 1.9\% did, while the average absolute error of the highest-probability model decreased from 0.03 after the first run to 0.007 after the second subdivision.
+In addition, the initial grid had 400 boxes, the singly subdivided grid 164, and the final grid (4x initial resolution) had 144, meaning the overall additional computational effort to quadruple the fit precision was less than producing the initial simulation set.
 
   \subsection{SnS Solar Cell}
-    This example aims to demonstrate a more realistic application of \texttt{bayesim}, i.e.
+    This example demonstrates a more realistic application of \texttt{bayesim}, i.e.
 when the model being used to compute likelihoods is more computationally expensive.
@@
       \includegraphics[width=0.8\columnwidth]{figure_4.png}
-      \caption{PMFs produced by \texttt{bayesim}, after initial run and after one subdivision (Blue and green, respectively).
+      \caption{PMFs produced by \texttt{bayesim}, after initial run and after one subdivision (blue and green, respectively).
 In red, PMF from Reference~\cite{SnSJoule}.
@@
 \section*{Acknowledgements}
-R.C.K.
-acknowledges the funding of a Blue Waters Graduate Fellowship.
-The SnS work referenced in~\cite{SnSJoule} was funded by a Google Faculty Research Award, as well as the Center for Next Generation Materials by Design (CNGMD), an Energy Frontier Research Center funded by the U.S.
-Department of Energy, Office of Science, Basic Energy Sciences.
+R.C.K. acknowledges the funding of a Blue Waters Graduate Fellowship. This work was supported by a TOTAL SA research grant funded through MIT\text{ei}, the MIT Energy Initiative.
 

### 2018-09-10 bayesim/utils.py

@@ -2,10 +2,10 @@ from copy import deepcopy
 import numpy as np
 import pandas as pd
 import sys
-#sys.path.append('../../')
+sys.path.append('../../')
 #import bayesim.params as pm
 #import bayesim.model as bym
-#import model as bym
+import model as bym
 #import bayesim.pmf as pmf
 import matplotlib.pyplot as plt
 import matplotlib.patches as mplp
@@ -74,11 +74,12 @@ def visualize_PMF_sequence(statefile_list, **argv):
                                 else:
                                     y = 0.8-(float(j)/float(len(axes_sets)))*0.7
                                 axes[rownum][colnum].add_patch(mplp.Rectangle((x,y), 0.1, 0.1, facecolor=colors[j]))
-                                axes[rownum][colnum].text(x+0.15, y, name_list[j], color='k', fontsize=20)
+                                axes[rownum][colnum].text(x+0.15, y+0.01, name_list[j], color='k', fontsize=20)
                             if plot_true_vals:
-                                axes[rownum][colnum].scatter([0.16],[0.1],200,'#FFFF00',marker='*')
-                                axes[rownum][colnum].scatter([0.25],[0.1],200,c="None",marker='o',linewidths=3,edgecolors='#FFFF00')
-                                axes[rownum][colnum].text(0.35, 0.1, 'true values', color='k', fontsize=20)
+                                axes[rownum][colnum].add_patch(mplp.Rectangle((0.13,0.06), 0.17, 0.08, facecolor='0.8'))
+                                axes[rownum][colnum].scatter([0.16],[0.1],200, '#FFFF00', marker='*', zorder=200)
+                                axes[rownum][colnum].scatter([0.25],[0.1],200, c="None", marker='o', linewidths=3, edgecolors='#FFFF00', zorder=200)
+                                axes[rownum][colnum].text(0.35, 0.08, 'ground truth', color='k', fontsize=20)
                         else:
                             fig.delaxes(axes[rownum][colnum])
                     else:

### 2018-10-10 paper/Manuscript.tex
committing before repackaging

@@
 We discuss the implementation choices made in the code, showcase two examples in photovoltaics, and discuss general prerequisites for the approach to apply to other systems.
-
-  [Target journal: Computer Physics Communications]
 \end{abstract}
@@
      \label{Eq:1001}
-     P(H|E)=\frac{P(H)P(E|H)}{P(E)}
+     P(H|E)=\frac{P(H)P(E|H)}{P(E)},
    \end{split}
@@
      \label{Eq:2}
-     P(H|\{E_1,E_2,...E_n\}) = \frac{P(H|\{E_1,E_2...E_{n-1}\})P(E_n|H)}{P(E_n)}
+     P(H|\{E_1,E_2,...E_n\}) = \frac{P(H|\{E_1,E_2...E_{n-1}\})P(E_n|H)}{P(E_n)},
    \end{split}
@@
 
- A high-level summary of what \texttt{bayesim} does is shown in ~\autoref{fig1}.
-Part (a) is a flowchart showing that observed (as a function of experimental conditions $\{C\}$ and simulated (as a function of fitting parameters $\{P\}$ and experimental conditions $\{C\}$) outputs are compared to produce a probability distribution over $\{P\}$.
-Part (b) schematically indicates the adaptive grid sampling approach for a hypothetical two-dimensional parameter space, wherein grid boxes exceeding some threshold probability are subdivided and lower-probability regions discarded, allowing attainment of a high fitting precision without needing to sample the entire parameter space at the same high density.
+ A high-level summary of what \texttt{bayesim} does is shown in ~\autoref{fig1}a.
+The flowchart shows that observed (as a function of experimental conditions $\{C\}$ and simulated (as a function of fitting parameters $\{P\}$ and experimental conditions $\{C\}$) outputs are compared to produce a probability distribution over $\{P\}$.
+~\autoref{fig1}b schematically indicates the adaptive grid sampling approach for a hypothetical two-dimensional parameter space, wherein grid boxes exceeding some threshold probability are subdivided and lower-probability regions discarded, allowing attainment of a high fitting precision without needing to sample the entire parameter space at the same high density.
 
@@
     \begin{equation}
-      J(V,T) = J_L+J_0\left(\exp{\frac{qV}{nkT}}-1\right)
+      J(V,T) = J_L+J_0\left(\exp{\frac{qV}{nkT}}-1\right),
       \label{ID_eqn}
@@
     \begin{equation}
-      J_0 \approx B'T^{3/n}\exp{\left(\frac{-E_{g0}}{nkT}\right)}
+      J_0 \approx B'T^{3/n}\exp{\left(\frac{-E_{g0}}{nkT}\right)},
     \end{equation}
@@
 In addition, on the first inference run (prior to any subdivision), an average of 45\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 1.9\% did, while the average absolute error of the highest-probability model decreased from 0.03 after the first run to 0.007 after the second subdivision.
+
     In addition, the initial grid had 400 boxes, the singly subdivided grid 164, and the final grid (4x initial resolution) had 144, meaning the overall additional computational effort to quadruple the fit precision was less than producing the initial simulation set.
+In comparison, using a ``brute-force'' grid approach, reaching 4x precision would take $4^n$ times the computational load in $n$ dimensions, i.e.
+16x for this case.
+The exact factor of improvement is problem-dependent, but in all cases the load is significantly less than the exponential scaling of the prior approach.
 
@@
 the diffusion length), is constrained, emerges just as clearly.
+The differences in fitted values stem from the fact that the prior published analysis didn't account for model uncertainty, while this feature is included in \texttt{bayesim}.
+For more details on this, see the Supporting Information.
 
@@
 \bibliography{biblio}
-\bibliographystyle{ieeetr}
+\bibliographystyle{plainurl}
 

### 2018-10-10 docs/conf.py

@@ -28,7 +28,7 @@ author = 'Rachel C Kurchin and Giuseppe Romano'
 # The short X.Y version
 version = ''
 # The full version, including alpha/beta/rc tags
-release = '0.9.1'
+release = '0.9.5'
 
 
 # -- General configuration ---------------------------------------------------

### 2018-10-10 setup.py

@@ -1,14 +1,12 @@
-from setuptools import setup,find_packages
+from setuptools import setup, find_packages
 import os
 
-
 setup(name='bayesim',
-      version='0.9.4',
+      version='0.9.5',
       description='Fast model fitting via Bayesian inference',
       author='Rachel Kurchin, Giuseppe Romano',
       author_email='rkurchin@mit.edu, romanog@mit.edu',
-      classifiers=['Programming Language :: Python :: 2.7',\
-                   'Programming Language :: Python :: 3.6'],
+      classifiers=['Programming Language :: Python :: 3.6'],
       long_description=open('README.rst').read(),
       install_requires=['pandas',
                         'deepdish',

### 2018-10-10 paper/Manuscript.tex
updating paper

@@
 
-    The lower part of ~\autoref{ID_data} shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating.
+    ~\autoref{ID_data}b shows the posterior distributions after the first inference run and after each round of subdivision, demonstrating that \texttt{bayesim} gets progressively closer to the ``true" values as the loop continues iterating.
 In addition, on the first inference run (prior to any subdivision), an average of 45\% of grid points had larger model uncertainty than experimental uncertainty, while after the second subdivision, only 1.9\% did, while the average absolute error of the highest-probability model decreased from 0.03 after the first run to 0.007 after the second subdivision.
@@
 The differences in fitted values stem from the fact that the prior published analysis didn't account for model uncertainty, while this feature is included in \texttt{bayesim}.
-For more details on this, see the Supporting Information.
 
@@
  would be amenable to \texttt{bayesim}.
-The online documentation page~\cite{docs} maintains a list of examples which will grow as the authors become aware of/implement more, and the latest version of the code can always be found in the Github repository~\cite{gh}.
-The online documentation also hosts other useful information, such as detailed documentation of every class and function in \texttt{bayesim}, a more extensive technical background section than is included here, and an updated manual for usage of the code.
+The online documentation page~\cite{docs} maintains a list of examples which will grow as the authors become aware of/implement more.
+The latest version of the code can always be found in the Github repository~\cite{gh}, and the most recent stable and thoroughly-tested version is installable via PyPI~\cite{pypi}.
+The online documentation also hosts other useful information, such as detailed documentation of every class and function in \texttt{bayesim}, a more extensive technical background section than is included here, a list of planned future features, and an updated manual for usage of the code.
 

### 2019-05-30 docs/_build/latex/bayesim.tex
fixed deepdish issue and some other little bugs with PMF averaging, etc.

%% Generated by Sphinx.
\def\sphinxdocclass{report}
\documentclass[letterpaper,10pt,english]{sphinxmanual}
\ifdefined\pdfpxdimen
   \let\sphinxpxdimen\pdfpxdimen\else\newdimen\sphinxpxdimen
\fi \sphinxpxdimen=.75bp\relax

\PassOptionsToPackage{warn}{textcomp}
\usepackage[utf8]{inputenc}
\ifdefined\DeclareUnicodeCharacter
 \ifdefined\DeclareUnicodeCharacterAsOptional
  \DeclareUnicodeCharacter{"00A0}{\nobreakspace}
  \DeclareUnicodeCharacter{"2500}{\sphinxunichar{2500}}
  \DeclareUnicodeCharacter{"2502}{\sphinxunichar{2502}}
  \DeclareUnicodeCharacter{"2514}{\sphinxunichar{2514}}
  \DeclareUnicodeCharacter{"251C}{\sphinxunichar{251C}}
  \DeclareUnicodeCharacter{"2572}{\textbackslash}
 \else
  \DeclareUnicodeCharacter{00A0}{\nobreakspace}
  \DeclareUnicodeCharacter{2500}{\sphinxunichar{2500}}
  \DeclareUnicodeCharacter{2502}{\sphinxunichar{2502}}
  \DeclareUnicodeCharacter{2514}{\sphinxunichar{2514}}
  \DeclareUnicodeCharacter{251C}{\sphinxunichar{251C}}
  \DeclareUnicodeCharacter{2572}{\textbackslash}
 \fi
\fi
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amstext}
\usepackage{babel}
\usepackage{times}
\usepackage[Bjarne]{fncychap}
\usepackage{sphinx}

\usepackage{geometry}

% Include hyperref last.
\usepackage{hyperref}
% Fix anchor placement for figures with captions.
\usepackage{hypcap}% it must be loaded after hyperref.
% Set up styles of URL: it should be placed after hyperref.
\urlstyle{same}

\addto\captionsenglish{\renewcommand{\figurename}{Fig.}}
\addto\captionsenglish{\renewcommand{\tablename}{Table}}
\addto\captionsenglish{\renewcommand{\literalblockname}{Listing}}

\addto\captionsenglish{\renewcommand{\literalblockcontinuedname}{continued from previous page}}
\addto\captionsenglish{\renewcommand{\literalblockcontinuesname}{continues on next page}}

\addto\extrasenglish{\def\pageautorefname{page}}

\definecolor{firebrick}{rgb}{0.7, 0.13, 0.13} \definecolor{darkorange}{rgb}{1.0, 0.55, 0.0} \definecolor{darkmagenta}{rgb}{0.55, 0.0, 0.55}

\title{bayesim Documentation}
\date{Oct 31, 2018}
\release{0.9.5}
\author{Rachel C Kurchin and Giuseppe Romano}
\newcommand{\sphinxlogo}{\vbox{}}
\renewcommand{\releasename}{Release}
\makeindex

\begin{document}

\maketitle
\sphinxtableofcontents
\phantomsection\label{\detokenize{index::doc}}

\chapter{Getting Started}
\label{\detokenize{gettingstarted:getting-started}}\label{\detokenize{gettingstarted::doc}}

\section{Prerequisites}
\label{\detokenize{gettingstarted:prerequisites}}
\sphinxcode{\sphinxupquote{bayesim}} has been most thoroughly tested in Python 3.6.

\section{Download}
\label{\detokenize{gettingstarted:download}}
To install bayesim simply type

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
pip install bayesim
\end{sphinxVerbatim}

\section{Usage}
\label{\detokenize{gettingstarted:usage}}
For more details on both usage methods described below, see the {\hyperref[\detokenize{manual::doc}]{\sphinxcrossref{\DUrole{doc}{Manual}}}}.

\subsection{Python / Jupyter}
\label{\detokenize{gettingstarted:python-jupyter}}
The easiest way to learn how \sphinxcode{\sphinxupquote{bayesim}} works is by stepping through one of the {\hyperref[\detokenize{examples::doc}]{\sphinxcrossref{\DUrole{doc}{Examples}}}}, which have well-commented \sphinxhref{http://jupyter.org}{Jupyter notebooks} associated with them and can be run in \sphinxhref{https://mybinder.org}{binder} with no need to install Python, \sphinxcode{\sphinxupquote{bayesim}}, or any of its dependencies locally.

If you are comfortable coding in Python, these examples will also make it clear how to script using \sphinxcode{\sphinxupquote{bayesim}}.

\subsection{Command line}
\label{\detokenize{gettingstarted:command-line}}
A command line interface will be implemented in a future release!

\chapter{Why bayesim?}
\label{\detokenize{whybayesim:why-bayesim}}\label{\detokenize{whybayesim::doc}}
There are plenty of tools already out there for Bayesian parameter estimation. What’s special/useful about \sphinxcode{\sphinxupquote{bayesim}}? What is it good for? What \sphinxstyleemphasis{isn’t} it good for?

I won’t reinvent the wheel of the Bayesian/frequentist debate here because many smarter people have written a lot about it in other places. Instead, I’ll just emphasize a couple important points, the first of which is general to the approach, and the second of which is specific to how \sphinxcode{\sphinxupquote{bayesim}} implements it.

\section{Probability distributions are nice}
\label{\detokenize{whybayesim:probability-distributions-are-nice}}
The output of a \sphinxcode{\sphinxupquote{bayesim}} analysis is not just a set of values and uncertainties, but rather a full multidimensional probability distribution. The power of this comes when the regions of parameter space that have highest probability are not simple ellipsoidal blobs with axes along the parameter axes, but instead take on more complicated shapes that can reflect underlying tradeoffs between fitting parameters. For example, in our research group’s \sphinxhref{https://www.sciencedirect.com/science/article/pii/S254243511730096X}{first published paper using Bayesian parameter estimation} (which used a much earlier precursor of the code that was eventually developed into \sphinxcode{\sphinxupquote{bayesim}}), we found that of the four parameters we fit, two were constrained quite well, while two others didn’t seem to be on an individual basis:

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics{{SnS_probs}.png}
\caption{Figure 3 from \sphinxhref{https://www.sciencedirect.com/science/article/pii/S254243511730096X}{this paper}. The \(\Delta E_c\) and \(S_\text{eff}\) parameters are constrained well, while \(\mu\) and \(\tau\) exhibit a much larger spread in their individual distributions (red and yellow histograms).}\label{\detokenize{whybayesim:id1}}\end{figure}

However, when we look at the two-parameter marginalization of the final posterior distribution (second plot from the right on the bottom row), we see that while the values of \(\mu\) and \(\tau\) may not have been individually well-constrained, their \sphinxstyleemphasis{product} was pinned quite well. As it happens, this product is related to a quantity known as the \sphinxstyleemphasis{electron diffusion length}, and under the conditions we measured the solar cell, other effects that \(\mu\) and \(\tau\) have on performance were small enough that they couldn’t be decoupled from each other.

This type of insight could not be gleaned from a more traditional parameter fitting approach such as a least-squares regression and requires the ability to see the probability distribution over parameters.

\section{Simulations are expensive}
\label{\detokenize{whybayesim:simulations-are-expensive}}
A very common approach to multidimensional Bayesian parameter estimation involves Monte Carlo (MC) sampling rather than sampling on a grid as we do here. In general, such approaches scale very well to larger numbers of dimensions and hence may have great appeal (“larger numbers” is problem dependent but for “typical” problems if you have more than 10 parameters to estimate, an MC approach is preferable). Bayesim uses adaptive grid sampling, which has two major benefits over MC sampling for relatively low-dimensional problems:
\begin{enumerate}
\item {}
It can be significantly less computationally expensive (from a more formal numerical perspective, it avoids the generally large prefactor in cost estimates for MC sampling, which can overwhelm the dimensional savings when the dimensionality is small) and

\item {}
There is significantly less uncertainty that all regions of non-negligible probability are quickly detected, since the coarsest iteration tends to identify all “hotspots” immediately, provided the {\hyperref[\detokenize{bayesics:model-uncertainty}]{\sphinxcrossref{\DUrole{std,std-ref}{model uncertainty}}}} associated with the sampling density is incorporated.

\end{enumerate}

The take-home message here is that \sphinxcode{\sphinxupquote{bayesim}}’s \sphinxstylestrong{approach shines in situations where the computational effort required to evaluate the likelihood is large, as when the data models are sophisticated numerical solvers, and the number of fitting parameters is (relatively) small.}

Many of the {\hyperref[\detokenize{examples::doc}]{\sphinxcrossref{\DUrole{doc}{Examples}}}} we show here involve analytical models, however. This is done only to create examples that are tractable to run in a few seconds on a typical personal computer. In reality, while \sphinxcode{\sphinxupquote{bayesim}} certainly works with these models, it is unlikely to be the most efficient approach to fitting their parameters. In addition, with an analytical model, tradeoffs such as the one between \(\mu\) and \(\tau\) described above are generally already apparent from the mathematical form of the model and hence the final probability distribution isn’t necessarily required for such insights.

\chapter{Technical Background}
\label{\detokenize{bayesics:technical-background}}\label{\detokenize{bayesics::doc}}
This page includes some references about Bayes’ Theorem and Bayesian inference and discusses the particulars of the implementation of these ideas within \sphinxcode{\sphinxupquote{bayesim}}.

\section{Bayes’ Theorem}
\label{\detokenize{bayesics:bayes-theorem}}
There are a \sphinxhref{https://brohrer.github.io/how\_bayesian\_inference\_works.html}{plethora} of \sphinxhref{https://brilliant.org/wiki/bayes-theorem/}{great} \sphinxhref{https://betterexplained.com/articles/an-intuitive-and-short-explanation-of-bayes-theorem/}{explanations} of Bayes’ Theorem out there already, so I won’t go through all the bayesics here but instead refer you to one of those linked above or any number of others you can find online or in a textbook.

Assuming you understand Bayes’ Theorem to your own satisfaction at this point, let’s remind ourselves of some \sphinxstylestrong{terminology}.
\begin{equation}\label{equation:bayesics:bayesics:0}
\begin{split}\color{firebrick} {P(H|E)} =
\frac{\color{darkorange} {P(H)}
\color{darkmagenta} {P(E|H)}}
{\color{teal} {P(E)}}\end{split}
\end{equation}
The \(\color{firebrick}{\mathbf{\text{posterior probability}}}\) of our hypothesis \(H\) given observed evidence \(E\) is the result of a Bayesian update to the \(\color{darkorange}{\mathbf{\text{prior}}}\) estimate of the probability of \(H\) given the \(\color{darkmagenta}{\mathbf{\text{likelihood}}}\) of observing \(E\) in a world where \(H\) is true and the probability of observing our \(\color{teal}{\mathbf{\text{evidence}}}\) in the first place.

\section{Bayesian Inference and Parameter Estimation}
\label{\detokenize{bayesics:bayesian-inference-and-parameter-estimation}}
\begin{sphinxadmonition}{note}{Note:}
I haven’t found an online explanation of this material at a not-excessively-mathy level (I firmly believe that you don’t need a lot of knowledge of mathematical terminology to understand this; it can really be done in a very visual way) so I wrote my own. If you know of another, please \sphinxhref{mailto:rkurchin@mit.edu}{send it to me} and I’d be happy to link to it here!

\sphinxstylestrong{Update!!} I found some nice explanations/examples in \sphinxhref{https://github.com/jakevdp/BayesianAstronomy}{this repo}! Check them out for some more material in addition to what I’ve included here.
\end{sphinxadmonition}

Most of the examples used to explain Bayes’ Theorem have two hypotheses to disginguish between (e.g. “is it raining?”: yes or no). However, to use Bayes’ Theorem for \sphinxstyleemphasis{parameter estimation}, which is the problem of interest here, we need to generalize to many more than two hypotheses, and those hypotheses may be about the values of multiple different parameters. In addition, we would like to incorporate many pieces of evidence, necessitating many iterations of the Bayesian calculation. These and other factors can make it confusing to conceptualize how to generalize the types of computations we do to estimate the probability of the answer to a yes-or-no question or a dice roll to a problem statement relevant to a more general scientific/modeling inquiry. I will walk through these factors here.

\subsection{Many hypotheses, in multiple dimensions}
\label{\detokenize{bayesics:many-hypotheses-in-multiple-dimensions}}
The first step is let our hypotheses \(H\) range over more than two values. That is, rather than having \(H_1\) = “yes, it is raining” and \(H_2\) = “no, it is not raining”, we would instead have something like \(H_1\) = “the value of parameter \(A\) is \(a_1\)“, \(H_2\) = “the value of parameter \(A\) is \(a_2\)“, etc. for as many \(a_n\) as we wanted to consider. While we could then in principle enumerate many different statements of Bayes’ Theorem of the form

\begin{eqnarray}
  \label{equation:bayesics:bayesics:1}
P(A=a_1|E) &=& \frac{P(A=a_1)P(E|A=a_1)}{P(E)} \\
P(A=a_2|E) &=& \frac{P(A=a_2)P(E|A=a_2)}{P(E)} \\
&...& \\
P(A=a_n|E) &=& \frac{P(A=a_n)P(E|A=A_n)}{P(E)}
\end{eqnarray}
this is quite cumbersome and so instead we will write
\begin{equation}\label{equation:bayesics:bayesics:2}
\begin{split}P(A|E) = \frac{P(A)P(E|A)}{P(E)}\end{split}
\end{equation}
with the understanding that this probability is not a single value but rather a function over all possible values of \(A\). This also allows the number of equations we have to write not to explode when we want to add another fitting parameter, and instead the probability function just to be defined over an additional dimension:
\begin{equation}\label{equation:bayesics:bayesics:3}
\begin{split}P(A,B|E) = \frac{P(A,B)P(E|A,B)}{P(E)}\end{split}
\end{equation}

\subsection{Iterative Bayesian updates}
\label{\detokenize{bayesics:iterative-bayesian-updates}}
The next step is to reframe Bayes’ Theorem as an explicitly iterative procedure. Imagine we’ve incorporated one piece of evidence \(E_1\), resulting in a posterior probability \(P(H|E_1)\). To update our posterior again given further observation \(E_2\), we simply let this \sphinxstyleemphasis{posterior} become our new \sphinxstyleemphasis{prior}:
\begin{equation}\label{equation:bayesics:bayesics:4}
\begin{split}P(H|\{E_1,E_2\}) = \frac{P(H|E_1)P(E_2|H)}{P(E_2)}\end{split}
\end{equation}
Hopefully now it’s easy to see that for \sphinxstyleemphasis{n} pieces of evidence, we can say that
\begin{equation}\label{equation:bayesics:bayesics:5}
\begin{split}P(H|\{E_1,E_2,...E_n\}) = \frac{P(H|\{E_1,E_2...E_{n-1}\})P(E_n|H)}{P(E_n)}\end{split}
\end{equation}

\subsection{Where does the likelihood come from?!? Data modeling!}
\label{\detokenize{bayesics:where-does-the-likelihood-come-from-data-modeling}}
At this point, it would be natural to say “Sure, that math all makes sense, but how do I actually \sphinxstyleemphasis{know} what that likelihood \(P(E|H)\) \sphinxstyleemphasis{is?!?}”

This is where having a \sphinxstylestrong{model} of our experimental observations comes in. This model could take many forms - it might be a simple analytical equation, or it might be a sophisticated numerical solver. The key traits are that it can accurately predict the outcome of a measurement on your system as as function of all relevant experimental conditions as well as fitting parameters of interest.

More specifically, suppose your measurement yields some output variable \(O\) as a function of various experimental conditions \{\(C\)\}. Then your evidence looks like
\begin{equation}\label{equation:bayesics:bayesics:6}
\begin{split}O(C_1, C_2,...C_n)\end{split}
\end{equation}
Suppose also that you have a set of model parameters \{\(P\)\} that you wish to know the values of. That means that your posterior distribution after \(m\) observations will look something like
\begin{equation}\label{equation:bayesics:bayesics:7}
\begin{split}P(P_1, P_2,...P_l|O_1,O_2...O_m)\end{split}
\end{equation}
where the hypotheses are sets of values of the parameters \{\(P\)\}, i.e., points in the fitting parameter space. Then your \sphinxstylestrong{model} must take the form
\begin{equation}\label{equation:bayesics:bayesics:8}
\begin{split}M(\{P_1, P_2,...P_l\},\{C_1, C_2,...C_n\}) = O\end{split}
\end{equation}
Given an observation \(O_m\) at conditions \{\(C_1^m,C_2^m,...C_n^m\)\} (where the \(m\) superscript indicates specific values of the conditions rather than their full ranges), we can compute the likelihood over all parameters \{\(P\)\} by evaluating our model for these conditions \{\(C^m\)\} and comparing the simulated outputs \{\(M(\{P\},\{C^m\})\)\} to the measured output \(O_m\). But then how do we know what probabilities to assign as a function of how much the measured and simulated outputs differ? Glad you asked…

\subsection{Experimental Uncertainty}
\label{\detokenize{bayesics:experimental-uncertainty}}
Our experimental measurement \(O_m\) will have some associated uncertainty \(\Delta O\), generally a known property of our equipment/measurement technique. Quantifying this uncertainty is key to understanding how to calculate likelihoods. Specifically, we need to introduce an \sphinxstylestrong{error model}. We’ll use a Gaussian distribution, a very common pattern for experimental errors in all kinds of measurements:
\begin{equation}\label{equation:bayesics:bayesics:9}
\begin{split}P(x) = \frac{1}{\sqrt{2\pi\sigma^2}}e^{-\frac{(x-\mu)^2}{2\sigma^2}}\end{split}
\end{equation}
where \(\mu\) is the \sphinxstylestrong{mean}, \(\sigma\) is the \sphinxstylestrong{standard deviation}, and the term in front of the exponential is just a normalizing constant (to make sure that the probability distribution integrates to 1). The distribution looks like this:

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics[scale=0.6]{{720px-Normal_Distribution_PDF}.png}
\caption{You can see the impact of the two parameters - a larger \(\sigma\) value makes the distribution wider, while \(\mu\) simply shifts the center. (Image from \sphinxhref{https://en.wikipedia.org/wiki/Normal\_distribution}{Wikipedia}.)}\label{\detokenize{bayesics:id2}}\end{figure}

What this means for our example is that our measurement of some value \(O_m^0\) for our output parameter \(O\) is converted to a distribution of possible “true” values for \(O_m\):
\begin{equation}\label{equation:bayesics:bayesics:10}
\begin{split}P(O_m) \propto \exp\left({-\frac{(O_m-O_m^0)^2}{2*\Delta O^2}}\right)\end{split}
\end{equation}
(I’m leaving off the normalization constant for convenience.)

\subsection{Model Uncertainty}
\label{\detokenize{bayesics:model-uncertainty}}\label{\detokenize{bayesics:id1}}
Of course, when our model function isn’t a simple analytical equation but rather a numerical solver of some sort, we can’t evaluate it on a continuous parameter space but we instead have to discretize the space into a grid and choose points on that grid at which to simulate. This introduces a so-called “model uncertainty” proportional to the magnitude of the variation in the model output as one moves around the fitting parameter space. This model uncertainty is calculated in \sphinxcode{\sphinxupquote{bayesim}} at each experimental condition for each point in the parameter space as the largest change in model output from that point to any of the immediately adjacent points.

Then, when we compute likelihoods, we use the sum of these two uncertainties as the standard deviation of our Gaussian.

Especially if the parameter space grid is coarse, incorporating this model uncertainty is critical - if the variation in output variable from one grid point to another is significantly larger than the experimental uncertainty but this uncertainty is used as the standard deviation, it is possible that likelihood could be computed as zero everywhere in the parameter space, just because the measured output corresponded to parameters between several of the chosen sample points. And that wouldn’t be very good.

\section{An illustrative example: Kinematics}
\label{\detokenize{bayesics:an-illustrative-example-kinematics}}
This probably all seems a bit abstract at this point, so illustrate how we do this in practice, let’s use a simple example. Suppose we want to estimate the value of \(g\), the acceleration due to gravity near Earth’s surface, and \(v_0\), the initial velocity of a vertically launched projectile (e.g. a ball tossed straight up), based on some measured data about the trajectory of the ball. We know from basic kinematics that the height of the ball as a function of time should obey (assuming that the projectile’s initial height is defined as 0)
\begin{equation}\label{equation:bayesics:bayesics:11}
\begin{split}y(t) = v_0t - \frac 12 gt^2\end{split}
\end{equation}
This function represents our \sphinxstylestrong{model} of the data we will measure and we can equivalently write
\begin{equation}\label{equation:bayesics:bayesics:12}
\begin{split}M(v_0, g; t) = v_0t - \frac 12 gt^2\end{split}
\end{equation}
where we’ve now explicitly delineated our parameters \(g\) and \(v_0\) and our measurement condition \(t\).

Now let’s suppose we make a measurement after 2 seconds of flight and find that \(y(2)=3\), with an uncertainty in the measurement of 0.2. Recalling our Gaussian error model from above, we can write
\begin{equation}\label{equation:bayesics:bayesics:13}
\begin{split}P(y(2)) \propto \exp\left({-\frac{(y(2)-3)^2}{2*0.2^2}}\right)\end{split}
\end{equation}
(Assume model uncertainty is negligible.) But what we \sphinxstyleemphasis{really} want is a probability distribution over our parameters, not over the measurement value itself. Fortunately, our model function lets us do just that! We can translate our distribution over possible measured values into one over possible parameter values using the model function:
\begin{eqnarray}
  \label{equation:bayesics:condprob}
P(v_0, g | y(2)=3 \pm 0.2) & \propto & \exp\left({-\frac{(M(v_0,g;2)-3)^2}{2*0.2^2}}\right) \\
& \propto & \exp\left({-\frac{(2v_0 - 2g - 3)^2}{0.08}}\right)
\end{eqnarray}
Now we can visualize what that distribution looks like in “\(v_0\)-\(g\)” space:

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics{{probs_1}.png}
\caption{On the left, the probability distribution over a wide range of possible values. On the right, zoomed in to near the true value of \(g\) to show Gaussian spread.}\label{\detokenize{bayesics:id3}}\end{figure}

Another way we might want to visualize would be in the space of what the actual trajectories look like:

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics{{trajs}.png}
\caption{On the left, \(y(t)\) trajectories from \(t=0\) to \(t=3\). On the right, zooming in on the region indicated to see spread around \sphinxtitleref{y(2)=3}.}\label{\detokenize{bayesics:id4}}\end{figure}

So we can see that what the inference step did was essentially “pin” the trajectories to go through (or close to) the measured point at (\sphinxstyleemphasis{t},*y*)=(2.0,3.0).

Now let’s suppose we take another measurement, a short time later: \sphinxstyleemphasis{y(2.3)=0.1}, but with a larger uncertainty, this time of 0.5. Now we return to Bayes’ Theorem - our prior distribution will be the conditional distribution from Equation \eqref{equation:bayesics:condprob} above, and the likelihood will be a new conditional distribution generated in exactly the same way but for this new data point. What does the posterior look like?

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics{{probs_2}.png}
\caption{(Note that the axis limits are smaller than above)}\label{\detokenize{bayesics:id5}}\end{figure}

As we would expect, we’re starting to zero in on a smaller region. And how about the trajectories?

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics{{trajs_2}.png}
\caption{Newly refined set of trajectories shown in red, overlaid on (paler) larger set from the previous step.}\label{\detokenize{bayesics:id6}}\end{figure}

As expected, we’ve further winnowed down the possible trajectories. If we continued this process for more and more measurements, eventually zeroing in on the correct values with greater and greater precision.

To see this example as implemented in \sphinxcode{\sphinxupquote{bayesim}}, check out the {\hyperref[\detokenize{examples::doc}]{\sphinxcrossref{\DUrole{doc}{Examples}}}} page!

\chapter{Manual}
\label{\detokenize{manual:manual}}\label{\detokenize{manual::doc}}

\section{Overview}
\label{\detokenize{manual:overview}}
The basic procedure of performing a parameter fit with \sphinxcode{\sphinxupquote{bayesim}} is as follows:

\begin{figure}[htbp]
\centering

\noindent\sphinxincludegraphics[scale=0.6]{{flowchart_b}.png}
\end{figure}

On this page, we will dive into each part of this flowchart in detail to understand what is happening and what options exist to tweak \sphinxcode{\sphinxupquote{bayesim}}’s behavior. The code snippets will be assuming that we are modeling a solar cell’s output current \(J\) with two experimental conditions: voltage \(V\) and temperature \(T\).

The first step is to initialize a \sphinxcode{\sphinxupquote{Model}} object. Several of the next steps can be rolled into this initialization using keywords, but the only required input is the name of the output variable. For example:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{k+kn}{import} \PYG{n+nn}{bayesim.model} \PYG{k+kn}{as} \PYG{n+nn}{bym}
\PYG{n}{m} \PYG{o}{=} \PYG{n}{bym}\PYG{o}{.}\PYG{n}{Model}\PYG{p}{(}\PYG{n}{output\PYGZus{}var}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{J}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

\section{Attaching Observations}
\label{\detokenize{manual:attaching-observations}}\label{\detokenize{manual:attach-obs}}
The experimental observations should reside in an HDF5 file with columns for each experimental condition and the output variable. Optionally, there may also be a column for experimental uncertainty. In addition, one should specify one of the experimental conditions (EC’s) to be plotted on the x-axis when visualizing data later on using the \sphinxcode{\sphinxupquote{ec\_x\_var}} keyword. The data are attached using:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{attach\PYGZus{}observations}\PYG{p}{(}\PYG{n}{obs\PYGZus{}data\PYGZus{}path}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{obs\PYGZus{}data.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{ec\PYGZus{}x\PYGZus{}var}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{V}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

If this column isn’t present, the \sphinxcode{\sphinxupquote{fixed\_unc}} keyword must be passed with a value to use as experimental uncertainty for every data point:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{attach\PYGZus{}observations}\PYG{p}{(}\PYG{n}{obs\PYGZus{}data\PYGZus{}path}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{obs\PYGZus{}data.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{ec\PYGZus{}x\PYGZus{}var}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{V}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{fixed\PYGZus{}unc}\PYG{o}{=}\PYG{l+m+mf}{0.02}\PYG{p}{)}
\end{sphinxVerbatim}

By default, to save computational time, \sphinxcode{\sphinxupquote{bayesim}} will not import all data points, but rather attempt to maintain some minimum spacing between points such that each piece of evidence is more likely to contribute to constraining the posterior distribution. This behavior can be turned off by passing \sphinxcode{\sphinxupquote{keep\_all=True}} to the \sphinxcode{\sphinxupquote{attach\_observations()}} function, and can be tuned using the \sphinxcode{\sphinxupquote{max\_ec\_x\_step}} and \sphinxcode{\sphinxupquote{thresh\_dif\_frac}} keywords. \sphinxcode{\sphinxupquote{thresh\_dif\_frac}} is given as a fraction of the range of values of the output variable and defaults to 0.01. It defines the minimum difference in output variable along the x-axis EC (at fixed values of the other EC’s) for which to save a point. \sphinxcode{\sphinxupquote{max\_ec\_x\_step}} is the largest step to take in the previously defined x-axis EC before saving a point anyway even if it \sphinxstyleemphasis{doesn’t} differ by that threshold amount, and defaults to 5\% of the range of values of the x-axis EC. Let’s look at an example case where we use the default values for these parameters:

\begin{figure}[htbp]
\centering
\capstart

\noindent\sphinxincludegraphics{{import_example}.png}
\caption{Note how in the ‘flatter’ region of the curve, the spacing along the x-axis of imported points is wider than in the ‘steeper’ region.}\label{\detokenize{manual:id1}}\end{figure}

\section{Defining Parameters}
\label{\detokenize{manual:defining-parameters}}
It is possible to predefine the parameter grid by directly constructing a \sphinxcode{\sphinxupquote{Param\_list}} object and passing it to the \sphinxcode{\sphinxupquote{Model}} constructor, although this is not necessary, because \sphinxcode{\sphinxupquote{bayesim}} is capable of determining these directly from the model data file (see next step). However, if one wants to use \sphinxcode{\sphinxupquote{bayesim}} to generate the list of model points that need to be simulated, this approach is useful. Consider the {\hyperref[\detokenize{examples:id}]{\sphinxcrossref{\DUrole{std,std-ref}{ideal diode}}}} example, where the parameters to be fit were \(B'\) and \(n\):

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{k+kn}{import} \PYG{n+nn}{bayesim.model} \PYG{k+kn}{as} \PYG{n+nn}{bym}
\PYG{k+kn}{import} \PYG{n+nn}{bayesim.params} \PYG{k+kn}{as} \PYG{n+nn}{byp}
\PYG{n}{pl} \PYG{o}{=} \PYG{n}{byp}\PYG{o}{.}\PYG{n}{Param\PYGZus{}list}\PYG{p}{(}\PYG{p}{)}
\PYG{n}{pl}\PYG{o}{.}\PYG{n}{add\PYGZus{}fit\PYGZus{}param}\PYG{p}{(}\PYG{n}{name}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{Bp}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{display\PYGZus{}name}\PYG{o}{=}\PYG{l+s+s2}{\PYGZdq{}}\PYG{l+s+s2}{B}\PYG{l+s+s2}{\PYGZsq{}}\PYG{l+s+s2}{\PYGZdq{}}\PYG{p}{,} \PYG{n}{val\PYGZus{}range}\PYG{o}{=}\PYG{p}{[}\PYG{l+m+mi}{10}\PYG{p}{,}\PYG{l+m+mi}{1000}\PYG{p}{]}\PYG{p}{,} \PYG{n}{spacing}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{log}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{length}\PYG{o}{=}\PYG{l+m+mi}{20}\PYG{p}{,} \PYG{n}{units}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{arb.}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\PYG{n}{pl}\PYG{o}{.}\PYG{n}{add\PYGZus{}fit\PYGZus{}param}\PYG{p}{(}\PYG{n}{name}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{n}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{val\PYGZus{}range}\PYG{o}{=}\PYG{p}{[}\PYG{l+m+mi}{1}\PYG{p}{,}\PYG{l+m+mi}{2}\PYG{p}{]}\PYG{p}{,} \PYG{n}{length}\PYG{o}{=}\PYG{l+m+mi}{20}\PYG{p}{,} \PYG{n}{min\PYGZus{}width}\PYG{o}{=}\PYG{l+m+mf}{0.01}\PYG{p}{)}
\PYG{n}{m} \PYG{o}{=} \PYG{n}{bym}\PYG{o}{.}\PYG{n}{Model}\PYG{p}{(}\PYG{n}{params}\PYG{o}{=}\PYG{n}{pl}\PYG{p}{,} \PYG{n}{output\PYGZus{}var}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{J}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

The code block above sets the ranges of values, spacing (linear by default, logarithmic as an option), and number of divisions (10 by default) for the two parameters, and initializes the model object using this parameter grid. We can also set a display name for plot labeling (TeX input is accepted in this field), units (also used in plotting, defaults to ‘unitless’), and minimum width beyond which a grid box won’t be subdivided along this dimension (defaults to 1\% of the value range in the appropriate spacing). Some of these parameters can also be set after data import using the \sphinxcode{\sphinxupquote{set\_param\_info()}} function, as in:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{set\PYGZus{}param\PYGZus{}info}\PYG{p}{(}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{J}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{units}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{mA/cm\PYGZdl{}\PYGZca{}2\PYGZdl{}}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\PYG{n}{m}\PYG{o}{.}\PYG{n}{set\PYGZus{}param\PYGZus{}info}\PYG{p}{(}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{T}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{display\PYGZus{}name}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{temperature}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{units}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{K}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

\section{Attaching Modeled Data}
\label{\detokenize{manual:attaching-modeled-data}}
Next, we need to attach the modeled data. If you’re using \sphinxcode{\sphinxupquote{bayesim}} to tell your model what points to run, you can call \sphinxcode{\sphinxupquote{list\_model\_pts\_to\_run()}} to write out an HDF5 file to pass to your forward model:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{list\PYGZus{}model\PYGZus{}pts\PYGZus{}to\PYGZus{}run}\PYG{p}{(}\PYG{n}{fpath}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{model\PYGZus{}inputs.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

You can also directly interface with your model by passing a Python callable, as in:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{attach\PYGZus{}model}\PYG{p}{(}\PYG{n}{mode}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{function}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{model\PYGZus{}data\PYGZus{}func}\PYG{o}{=}\PYG{n}{model\PYGZus{}func}\PYG{p}{)}
\end{sphinxVerbatim}

where \sphinxcode{\sphinxupquote{model\_func}} is a callable in your namespace that accepts dictionaries of inputs, one with keys of the EC’s and one of the fitting parameters (see {\hyperref[\detokenize{examples:id}]{\sphinxcrossref{\DUrole{std,std-ref}{ideal diode}}}} example).

However, typically, the model data will be precomputed and residing in an HDF5 file which will be attached to the model object:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{attach\PYGZus{}model}\PYG{p}{(}\PYG{n}{mode}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{file}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{model\PYGZus{}data\PYGZus{}path}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{model\PYGZus{}data.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

The {\hyperref[\detokenize{bayesics:model-uncertainty}]{\sphinxcrossref{\DUrole{std,std-ref}{model uncertainty}}}} also needs to be computed. This can be done either with a separate function call to \sphinxcode{\sphinxupquote{calc\_model\_unc()}}, or in a single step when attaching the model data:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{attach\PYGZus{}model}\PYG{p}{(}\PYG{n}{mode}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{file}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{model\PYGZus{}data\PYGZus{}path}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{model\PYGZus{}data.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{,} \PYG{n}{calc\PYGZus{}model\PYGZus{}unc}\PYG{o}{=}\PYG{n+nb+bp}{True}\PYG{p}{)}
\end{sphinxVerbatim}

The model uncertainty calculation can be somewhat expensive for large grids and will be parallelized by default on Unix-based systems.

\section{Performing the Inference}
\label{\detokenize{manual:performing-the-inference}}
Once experimental and model data and their associated uncertainties have been defined and the fitting parameters either explicitly specified or determined from the data, we can do Bayesian inference! The inference is performed by the \sphinxcode{\sphinxupquote{run()}} function. Details about what calculations are actually done and what they mean can be found on the {\hyperref[\detokenize{bayesics::doc}]{\sphinxcrossref{\DUrole{doc}{Technical Background}}}} page; here we will focus on the mechanics of the code.

First, a bounded uniform prior (equal probability in every grid box) is defined. Next, a piece of evidence (one experimental measurement, i.e. in this example a \((V, T, J)\) tuple) is chosen at random. The likelihood at each point in parameter space is computed conditioned on this piece of evidence as a Gaussian in the difference between the measured output and the simulated output at that point, with a standard deviation equal to the sum of the experimental error for that observation and the model uncertainty at that point:
\begin{equation}\label{equation:manual:manual:0}
\begin{split}\mathcal{P}(\{P\}|O_e(\{c\}_i)) \propto \exp\left(\frac{-(O_e(\{c\}_i)-O_m(\{P\},\{c\}_i))^2}{2(\sigma_e(\{c\}_i)+\sigma_m(\{P\},\{c\}_i))^2}\right)\end{split}
\end{equation}
In the {\hyperref[\detokenize{examples:id}]{\sphinxcrossref{\DUrole{std,std-ref}{ideal diode}}}} example, this means more specifically that
\begin{equation}\label{equation:manual:manual:1}
\begin{split}\mathcal{P}(B',n|J_{\text{meas}}(V_i,T_i)) \propto \exp\left(\frac{-(J_{\text{meas}}(V_i,T_i)-J_{\text{mod}}(B',n,V_i,T_i))^2}{2(\sigma_\text{meas}(V_i,T_i)+\sigma_{\text{mod}}(B',n,V_i,T_i))^2}\right)\end{split}
\end{equation}
This likelihood is multiplied with the prior and normalized to compute the posterior.

Next, \sphinxcode{\sphinxupquote{bayesim}} will check if the posterior distribution is “concentrated” enough. This concentration is defined by two optional parameters passed to \sphinxcode{\sphinxupquote{run()}}, \sphinxcode{\sphinxupquote{th\_pm}} and \sphinxcode{\sphinxupquote{th\_pv}}, both on the interval (0,1) and defaulting to 0.9 and 0.05, respectively. The posterior is sufficiently concentrated is \sphinxcode{\sphinxupquote{th\_pm}} of the probability mass resides in \sphinxcode{\sphinxupquote{th\_pv}} of the parameter space. (Entropy-based thresholding is planned as an option for a future release)

If the posterior is not sufficiently concentrated, the posterior is set to the prior, another piece of evidence chosen, and another Bayesian update performed until it is. Once the concentration threshold is met, the posterior is saved and another check is done for whether enough pieces of evidence have been used. The requisite number to use is defined by the \sphinxcode{\sphinxupquote{min\_num\_pts}} keyword in the \sphinxcode{\sphinxupquote{run()}} function and defaults to 80\% of the total number of observation data points imported. If not enough points have been used, the current posterior is saved, a new uniform prior is set and the process above repeated as many times as necessary for sufficient points to be used. The final posterior is then the average of all computed posteriors. \sphinxcode{\sphinxupquote{bayesim}} will inform you how many posteriors were averaged and how many observed data points were used.

\section{Visualizing the Output}
\label{\detokenize{manual:visualizing-the-output}}
\sphinxcode{\sphinxupquote{bayesim}} has a variety of capacities for data visualization.

\subsection{Plotting the PMF}
\label{\detokenize{manual:plotting-the-pmf}}
Visualizing the posterior distribution (probability mass function, or PMF) is done using the \sphinxcode{\sphinxupquote{visualize\_probs()}} function. It takes an optional argument of a filepath to save the image, and can also highlight a specific point in the parameter space to compare to using the \sphinxcode{\sphinxupquote{true\_vals}} keyword.

\subsection{Visualizing the Grid}
\label{\detokenize{manual:visualizing-the-grid}}
To visualize the current state of the parameter space grid, use \sphinxcode{\sphinxupquote{visualize\_grid()}}, which can also accept a path to save the imge as well as the \sphinxcode{\sphinxupquote{true\_vals}} keyword to highlight a particular point.

\subsection{Comparing the Data}
\label{\detokenize{manual:comparing-the-data}}
The \sphinxcode{\sphinxupquote{comparison\_plot()}} function can directly compare modeled to simulated data. It will produce a number of plots with the output variable on the y-axis and the previously specified EC x-variable on the x-axis. It accepts a few optional keywords:
\begin{description}
\item[{\sphinxcode{\sphinxupquote{ec\_vals}}}] \leavevmode
dict or list of dict, specific experimental
conditions at which to plot (values for x-axis EC are ignored)

\item[{\sphinxcode{\sphinxupquote{num\_ecs}}}] \leavevmode
int, number of (randomly chosen) EC’s at which to plot
(ignored if previous option is provided)

\item[{\sphinxcode{\sphinxupquote{num\_param\_pts}}}] \leavevmode
int, number of parameter space points for which to plot
modeled data (will choose the most probable)

\end{description}

In addition to a filepath to save the image as well as a flag to return average errors.

\section{Subdividing the Grid}
\label{\detokenize{manual:subdividing-the-grid}}
Once you have taken a look at your posterior PMF and compared observed and highest-probability modeled data, you’ll have a sense for whether you’d like to go to a higher fit precision by subdividing the parameter space grid. This can be done via a call to the \sphinxcode{\sphinxupquote{subdivide()}} function, which accepts one optional argument of \sphinxcode{\sphinxupquote{threshold\_prob}}, the minimum probability for a box to have in order to be subdivided. It defaults to 0.001. \sphinxcode{\sphinxupquote{bayesim}} will then divide every grid box meeting this threshold \sphinxstyleemphasis{as well as every box immediately neighboring it} into two along every parameter dimension, unless it is already narrower than the minimum width defined for that parameter.

\sphinxcode{\sphinxupquote{bayesim}} will inform you how many boxes were subdivided and also automatically save a file of the new points that need to be simulated using the model in order to perform another inference run. This new model data can be attached exactly as described {\hyperref[\detokenize{manual:attach-obs}]{\sphinxcrossref{\DUrole{std,std-ref}{above}}}} using the \sphinxcode{\sphinxupquote{attach\_observations()}} function, and then inference can proceed again.

\section{Miscellaneous}
\label{\detokenize{manual:miscellaneous}}

\subsection{Saving a state file}
\label{\detokenize{manual:saving-a-state-file}}
At any point during an analysis, the state of your \sphinxcode{\sphinxupquote{Model}} object can be saved using the \sphinxcode{\sphinxupquote{save\_state()}} function, and can be reloaded again using keywords in the \sphinxcode{\sphinxupquote{Model}} constructor:

\fvset{hllines={, ,}}%
\begin{sphinxVerbatim}[commandchars=\\\{\}]
\PYG{n}{m}\PYG{o}{.}\PYG{n}{save\PYGZus{}state}\PYG{p}{(}\PYG{n}{filename}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{statefile.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\PYG{n}{m} \PYG{o}{=} \PYG{n}{bym}\PYG{o}{.}\PYG{n}{Model}\PYG{p}{(}\PYG{n}{load\PYGZus{}state}\PYG{o}{=}\PYG{n+nb+bp}{True}\PYG{p}{,} \PYG{n}{state\PYGZus{}file}\PYG{o}{=}\PYG{l+s+s1}{\PYGZsq{}}\PYG{l+s+s1}{statefile.h5}\PYG{l+s+s1}{\PYGZsq{}}\PYG{p}{)}
\end{sphinxVerbatim}

This is useful, e.g., if you’re working interactively and want to be able to pick up again later without rerunning all the same code, or if you’d like to continue work on a different machine.

\subsection{Handling missing data}
\label{\detokenize{manual:handling-missing-data}}
Sometimes things go run when running a large number of simulations. \sphinxcode{\sphinxupquote{bayesim}} can handle cases where simulated data is missing (see the {\hyperref[\detokenize{examples:sns}]{\sphinxcrossref{\DUrole{std,std-ref}{SnS example}}}}). When computing likelihoods, if the simulated data for the EC in question isn’t present, it will just use what the uniform distribution probability would be for that point. The output of the \sphinxcode{\sphinxupquote{run()}} function will inform you how many times this happened on average over each Bayesian loop.

\chapter{Examples}
\label{\detokenize{examples:examples}}\label{\detokenize{examples::doc}}
This page is a (growing) list of example applications of \sphinxcode{\sphinxupquote{bayesim}}, attempting to showcase the variety of applicability as well as ways to run the code.

\section{Ideal diode solar cell}
\label{\detokenize{examples:id}}\label{\detokenize{examples:ideal-diode-solar-cell}}
The most self-contained example. Available to run in two different ways:

\subsection{Jupyter notebook}
\label{\detokenize{examples:jupyter-notebook}}
To run in Jupyter:
\begin{itemize}
\item {}
Download the \sphinxhref{https://github.com/PV-Lab/bayesim}{Github repository} and run from your local machine using \sphinxhref{http://jupyter.org}{Jupyter}

\end{itemize}

OR
\begin{itemize}
\item {}
Run in the cloud using Binder! \sphinxhref{https://mybinder.org/v2/gh/pv-lab/bayesim/master?filepath=examples\%2Fdiode\%2Fideal\_diode.ipynb}{\sphinxincludegraphics{{/Users/rachelkurchin/Dropbox (MIT)/MIT/Bayes_Project/bayesim/docs/_build/doctrees/images/https/mybinder.org/badge.svg/badge}.svg}}

\end{itemize}

\subsection{Command line}
\label{\detokenize{examples:command-line}}
To run from the command line:
\begin{enumerate}
\item {}
Download the \sphinxhref{https://github.com/PV-Lab/bayesim}{Github repository} (e.g. using \sphinxcode{\sphinxupquote{git clone}}) to your local machine.

\item {}
Navigate to the folder \sphinxcode{\sphinxupquote{bayesim/examples/command\_line/}}.

\item {}
…to be continued…(this example is not completely working yet)

\end{enumerate}

\section{Kinematics}
\label{\detokenize{examples:kinematics}}
Probably the simplest example, explained on the {\hyperref[\detokenize{bayesics::doc}]{\sphinxcrossref{\DUrole{doc}{Technical Background}}}} page. It exists in the \sphinxhref{https://github.com/PV-Lab/bayesim}{Github repo} under \sphinxcode{\sphinxupquote{examples/kinematics/kinematics.py}} and you can run it all in one go from a terminal (\sphinxcode{\sphinxupquote{python kinematics.py}}) or step-by-step in an IDE like Spyder.

\section{Tin Sulfide (SnS) solar cell}
\label{\detokenize{examples:tin-sulfide-sns-solar-cell}}\label{\detokenize{examples:sns}}
An example using an actual numerical model \textendash{} in this case, reproducing the fit (from \sphinxhref{https://www.sciencedirect.com/science/article/pii/S254243511730096X}{this paper}) of four material and interface properties in a tin sulfide solar cell. Also in Jupyter notebook form:
\begin{itemize}
\item {}
Download the \sphinxhref{https://github.com/PV-Lab/bayesim}{Github repository} and run from your local machine using \sphinxhref{http://jupyter.org}{Jupyter}

\end{itemize}

OR
\begin{itemize}
\item {}
Run in the cloud using Binder! \sphinxhref{https://mybinder.org/v2/gh/pv-lab/bayesim/master?filepath=examples\%2FSnS\%2FSnS\_fitting.ipynb}{\sphinxincludegraphics{{/Users/rachelkurchin/Dropbox (MIT)/MIT/Bayes_Project/bayesim/docs/_build/doctrees/images/https/mybinder.org/badge.svg/badge}.svg}}

\end{itemize}

\chapter{Future Features}
\label{\detokenize{futurefeatures:future-features}}\label{\detokenize{futurefeatures::doc}}
On this page, we maintain a list of planned future features of \sphinxcode{\sphinxupquote{bayesim}}. They’re listed under a variety of categories, in loosely descending order of priority within each.

\section{Visualization}
\label{\detokenize{futurefeatures:visualization}}\begin{itemize}
\item {}
visualizing model uncertainty on parameter grid

\item {}
visualizing measured vs. simulated data with experimental and model uncertainty

\item {}
option to generate a plot of which particular observed data was used in an inference run

\end{itemize}

\section{Other New Capabilities}
\label{\detokenize{futurefeatures:other-new-capabilities}}\begin{itemize}
\item {}
option for entropy-based thresholding as well as \sphinxtitleref{th\_pm} and \sphinxtitleref{th\_pv} in \sphinxcode{\sphinxupquote{run()}} function

\item {}
capability to pass a DataFrame objects to \sphinxcode{\sphinxupquote{attach\_model()}} and \sphinxcode{\sphinxupquote{attach\_observations()}} functions instead of just filepaths

\item {}
multiple output variables

\item {}
completely “closed-loop” version of \sphinxcode{\sphinxupquote{run()}} function that does subdivision as well (need a way to save a handle to a model function for running new simulations)

\item {}
interpolation of simulated data

\item {}
alternative error models

\item {}
alternative initial sampling states other than grids

\end{itemize}

\section{Efficiency/Speedup}
\label{\detokenize{futurefeatures:efficiency-speedup}}\begin{itemize}
\item {}
speed up \sphinxcode{\sphinxupquote{list\_model\_pts\_to\_run()}} function

\item {}
do some more code profiling to identify other particularly slow functions/components

\item {}
more parallelism generally

\end{itemize}

\section{Interfaces}
\label{\detokenize{futurefeatures:interfaces}}\begin{itemize}
\item {}
finish developing command-line interface

\item {}
build a GUI!

\end{itemize}

\chapter{Citing bayesim}
\label{\detokenize{citingbayesim:citing-bayesim}}\label{\detokenize{citingbayesim::doc}}
If you use the code, please consider citing

{[}placeholder{]}

\noindent\sphinxincludegraphics{{overview_figure}.png}

\renewcommand{\indexname}{Index}
\printindex
\end{document}

### 2019-05-30 bayesim/model.py

@@ -378,7 +378,7 @@ class Model(object):
         calc_model_unc = argv.get('calc_model_unc', False)
 
         if verbose:
-            print('Attaching simulated data...\n')
+            print('Attaching simulated data...')
 
         if mode == 'file':
             # import and sort data on parameter values
@@ -403,8 +403,7 @@ class Model(object):
                     self.probs = Pmf()
 
             ## check that all EC's are present at all model points
-            # first get list of EC points from observed data (round off and sort values before comparison)
-            self.check_ecs(gb=param_points_grps)
+            self.check_ecs(gb=param_points_grps, verbose=verbose)
 
             # Generate self.probs if necessary
             if self.probs.is_empty:
@@ -450,30 +449,41 @@ class Model(object):
 
             self.model_data = pd.DataFrame.from_dict(vecs)
 
-        # reset index to avoid duplication
-        self.model_data.reset_index(inplace=True,drop=True)
-
-        #print('before rounding')
-        #print(self.model_data.head())
-
         # round EC's and generate groups
         rd_dct = {c.name:c.tol_digits for c in self.params.ecs}
         self.model_data = self.model_data.round(rd_dct)
 
         # round fit params - actually just force them to be members of the vals lists
-        print("Rounding model data...")
+        if verbose:
+            print("Rounding model data...")
         for p in self.params.fit_params:
             #self.model_data[p.name] = [p.get_closest_val(val) for val in self.model_data[p.name]]
             self.model_data[p.name] = Parallel(n_jobs=cpu_count())(delayed(get_closest_val)(val, p.vals) for val in self.model_data[p.name])
 
-        # generate groups
+
+        # drop any modeled data at EC's not measured
+        if verbose:
+            print("Removing modeled EC's that weren't measured...")
+        self.model_data_ecgrps = self.model_data.groupby(self.ec_names())
+        model_ecs = pd.DataFrame.from_records(data=self.model_data_ecgrps.groups.keys(), columns=self.ec_names()).sort_values(by=self.ec_names()).reset_index(drop=True)
+        merged_ecs = model_ecs.merge(self.ec_pts, on=self.ec_names(), how='left', indicator=True)
+        extra_pts = merged_ecs[merged_ecs._merge=='left_only']
+        print('there are '+str(len(extra_pts))+' extra points...here are a few:')
+        print(extra_pts.head())
+        extra_data = merged_ecs[merged_ecs._merge=='right_only']
+        if len(extra_data)>0:
[…]

### 2019-05-30 bayesim/pmf.py

@@ -97,12 +97,14 @@ class Pmf(object):
         d['params'] = [p.__dict__ for p in self.params]
         return d
 
-    def normalize(self):
+    def normalize(self, **argv):
         """Normalize overall PMF."""
         norm_const = self.points['prob'].sum()
+        verbose = argv.get('verbose', False)
         #print(norm_const,type(norm_const))
         if abs(norm_const)<1e-12:
-            print("Somehow the normalization constant was zero! To play it safe, I won't do anything.")
+            if verbose:
+                print("Somehow the normalization constant was zero! To play it safe, I won't do anything.")
         else:
             self.points['prob'] = [p/norm_const for p in self.points['prob']]
 
@@ -216,7 +218,7 @@ class Pmf(object):
         inds_to_drop.extend(all_out_check.index)
         return neighbor_points.drop(labels=inds_to_drop)
 
-    def subdivide(self, threshold_prob, include_neighbors=True):
+    def subdivide(self, threshold_prob, include_neighbors=True, **argv):
         """
         Subdivide all boxes with P > threshold_prob and assign "locally uniform" probabilities within each box. If include_neighbors is true, also subdivide all boxes neighboring those boxes.
 
@@ -225,9 +227,12 @@ class Pmf(object):
         Args:
             threshold_prob (`float`): probability above which a box should be retained
             include_neighbors (`bool`): whether to also subdivide all immediate neighbors to boxes meeting the threshold
+            verbose (`bool`): Verbosity, default false
         """
         num_divs = {p.name:2 for p in self.params} #dummy for now
 
+        verbose = argv.get('verbose', False)
+        
         # pick out the boxes that will be subdivided
         to_subdivide = self.points[self.points['prob']>threshold_prob]
         #print(len(to_subdivide))
@@ -260,7 +265,8 @@ class Pmf(object):
             if this_width <= p.min_width:
                 # don't divide along this direction
                 num_divs[p.name] = 1
-                print('Minimum width/factor of %s already satisfied for parameter %s, not subdividing in that direction!'%(p.get_val_str(p.min_width), p.name))
+                if verbose:
+                    print('Minimum width/factor of %s already satisfied for parameter %s, not subdividing in that direction!'%(p.get_val_str(p.min_width), p.name))
 
         # create new boxes (and delete old ones)
         new_boxes = []
@@ -300,7 +306,7 @@ class Pmf(object):
         self.points = self.points.reset_index(drop=True)
 
         # should be normalized already, but just in case:
[…]

### 2019-05-30 bayesim/utils.py

@@ -150,7 +150,7 @@ def get_closest_val(val, val_list):
     else:
        return before
 
-def calc_deltas(grp, inds, param_lengths, model_data, fit_param_names, probs, output_var):
+def calc_deltas(grp, inds, param_lengths, model_data, fit_param_names, probs, output_var, take_average):
     # construct matrix of output_var({fit_params})
     subset = deepcopy(model_data.loc[inds])
     # sort and reset index of subset to match probs so we can use the find_neighbor_boxes function if needed
@@ -194,11 +194,28 @@ def calc_deltas(grp, inds, param_lengths, model_data, fit_param_names, probs, ou
         with np.errstate(invalid='ignore'):
             winners[i]=np.fmax(deltas_here[tuple([Ellipsis]+[slice(None,mat.shape[i],None)]+[slice(None)]*(len(mat.shape)-i-1))],deltas_here[tuple([Ellipsis]+[slice(1,mat.shape[i]+1,None)]+[slice(None)]*(len(mat.shape)-i-1))])
 
-    grad = np.amax(winners,axis=0)
+    grad = np.amax(winners, axis=0)
+    if take_average:
+        avg = np.nanmean(grad) # compute average
+        grad = avg * np.ones(grad.shape) # replace every entry with average
 
     # save these values to the appropriate indices in the vector
     if is_grid:
-        return (grp, grad.flatten())
+        to_return = (grp, grad.flatten())
     else:
         # pick out only the boxes that exist
-        return (grp, grad[tuple([i for i in list([ind_lists[p] for p in fit_param_names])])])
+        to_return = (grp, grad[tuple([i for i in list([ind_lists[p] for p in fit_param_names])])])
+
+    # check for NaNs
+    to_check = to_return[1]
+    if np.any(np.isnan(to_check)):
+        if np.all(np.isnan(to_check)):
+            # uh-oh
+            raise ValueError("All the uncertainties here (" + str(grp) + ") are NaN! Help!")
+        else:
+            # replace NaN values with average of non-NaN values for this group
+            avg_unc = np.nanmean(to_check)
+            fixed = np.where(np.isnan(to_check), to_check, avg_unc)
+            to_return[1] = fixed
+
+    return to_return

### 2019-05-30 docs/conf.py

@@ -140,7 +140,7 @@ latex_elements = {
 
     # Additional stuff for the LaTeX preamble.
     #
-    # 'preamble': '',
+    'preamble': '\definecolor{firebrick}{rgb}{0.7, 0.13, 0.13} \definecolor{darkorange}{rgb}{1.0, 0.55, 0.0} \definecolor{darkmagenta}{rgb}{0.55, 0.0, 0.55}',
 
     # Latex figure (float) alignment
     #

### 2019-05-30 examples/SnS/helper_fcns.py

@@ -1,60 +1,0 @@
-from copy import deepcopy
-import pandas as pd
-import deepdish as dd
-import numpy as np
-import zipfile
-
-def get_new_data(model_obj, new_pts_path, new_data_path):
-    all_data_path = './sim_data_less_sparse.h5'
-
-    # unzip the larger data file
-    zip_ref = zipfile.ZipFile(all_data_path+'.zip', 'r')
-    zip_ref.extractall('.')
-    zip_ref.close()
-
-    new_pts = dd.io.load(new_pts_path)
-    all_data = dd.io.load(all_data_path)
-    new_grps = new_pts.groupby(model_obj.fit_param_names())
-    all_grps = all_data.groupby(model_obj.fit_param_names())
-
-    new_dEc = sorted(list(set(new_pts['dEc'])))
-    new_S_eff = sorted(list(set(new_pts['S_eff'])))
-    new_mu = sorted(list(set(new_pts['mu'])))
-    new_tau = sorted(list(set(new_pts['tau'])))
-    new_lists = [new_dEc, new_S_eff, new_mu, new_tau]
-
-    all_dEc = sorted(list(set(all_data['dEc'])))
-    all_S_eff = sorted(list(set(all_data['S_eff'])))
-    all_mu = sorted(list(set(all_data['mu'])))
-    all_tau = sorted(list(set(all_data['tau'])))
-    old_lists = [all_dEc, all_S_eff, all_mu, all_tau]
-
-    # map new values to old indices
-    ind_maps = [{},{},{},{}]
-    for i in range(len(new_lists)):
-        for new_val in new_lists[i]:
-            diffs = [abs(new_val-old_val) for old_val in old_lists[i]]
-            min_ind = diffs.index(min(diffs))
-            ind_maps[i][new_val] = min_ind
-        #diffs = np.diff(list(ind_maps[i].values()))
-        #if any([d==1 for d in diffs]):
-        #    print('Might be out of range!'+str(ind_maps[i]))
-
-    # map new values onto unrounded sim points
-    key_map = {}
-    for new_key in list(new_grps.groups.keys()):
-        old_key = [-1, -1, -1, -1]
-        for i in range(len(model_obj.params.fit_params)):
-            old_key[i] = old_lists[i][ind_maps[i][new_key[i]]]
-        key_map[new_key] = tuple(old_key)
-    keys_to_keep = key_map.values()
-
-    new_data = deepcopy(all_data)
-    inds_to_drop = []
[…]

### 2019-05-30 examples/kinematics/kinematics.py

@@ -1,89 +1,0 @@
-import numpy as np
-import sys
-import math
-import pandas as pd
-sys.path.append('../../')
-import bayesim.model as bym
-import bayesim.params as byp
-import deepdish as dd
-import matplotlib.pyplot as plt
-
-# First, define our model
-def model_y(ec, params):
-    """
-    Simple model of a kinematic trajectory.
-
-    Args:
-        ec (`dict`): dictionary with a key 't' leading to a float value
-        params (`dict`): dictionary with keys 'v0' and 'g' leading to float values
-
-    Returns:
-        float: y-value at the given time assuming the given parameters
-    """
-    # read in the inputs
-    t = ec['t']
-    v0 = params['v0']
-    g = params['g']
-
-    # compute and return
-    return v0*t - 0.5 * g * t**2
-
-# describe our parameters
-pl = byp.Param_list()
-pl.add_fit_param(name='v0', val_range=[0,20], units='m/s')
-pl.add_fit_param(name='g', val_range=[0,20], units='m/s^2')
-pl.add_ec(name='t', units='s', is_x=True) # plot this on the x-axis
-pl.add_output(name='y', units='m')
-
-# the first two "observations"
-data = pd.DataFrame()
-data['t'] = [2, 2.3]
-data['y'] = [3, 0.1]
-data['uncertainty'] = [0.2, 0.5]
-dd.io.save('two_points.h5', data)
-
-# initialize bayesim model object
-m = bym.Model(params=pl, obs_data_path='two_points.h5', model_data_func=model_y, calc_model_unc=True)
-
-m.run()
-
-m.visualize_probs(fpath='two_obs_probs.png')
-
-# now let's add some more "observed" data by just generating it using our model function and some parameter values consistent with what we've done so far
-data = pd.DataFrame()
-t_vals = np.arange(0,3,0.1)
-y_vals = [model_y({'t':t},{'v0':11.31,'g':9.81}) for t in t_vals]
-data['t'] = t_vals
-data['y'] = y_vals
-dd.io.save('obs_data.h5',data)
-
-# initialize bayesim model object again, now with more data (and assuming the larger uncertainty value for all the points)
-m = bym.Model(params=pl, obs_data_path='obs_data.h5', model_data_func=model_y, calc_model_unc=True, fixed_unc=0.5)
-
-# run, using all data points
[…]

### 2019-05-30 paper/manuscript.py

@@ -1,103 +1,0 @@
-from pypapers.manuscript import Manuscript as M
-
-p = M(biblio_file ='biblio.bib', journal='prl', numberline=False, twocolumn=False)
-
-DMSE = r'''Department of Materials Science \& Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'''
-MechE = r'''Department of Mechanical Engineering, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA'''
-
-p.author(r'''Rachel Kurchin''',[DMSE])
-p.author('Giuseppe Romano',[MechE])
-p.author('Tonio Buonassisi',[MechE], email='buonassi@mit.edu')
-
-
-fig_1 = p.get_new_figure_label()
-fig_2 = p.get_new_figure_label()
-fig_3 = p.get_new_figure_label()
-fig_4 = p.get_new_figure_label()
-
-nn1 = p.get_new_equation_label()
-nn2 = p.get_new_equation_label()
-nn3 = p.get_new_equation_label()
-nn4 = p.get_new_equation_label()
-
-p.alias(r'''\kappa_{\mathrm{eff}}''','keff')
-
-
-p.title(r'''\texttt{bayesim}: a tool for fast model fitting with Bayesian inference''')
-
-p.abstract(r'''Target journal: Computer Physics Communications''')
-
-p.section('Introduction')
-
-#p.s('motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding), add some stuff about how semiconductor device community lags behind many others in model tuning, etc.')
-p.s('There are a plethora of examples across diverse scientific and engineering fields of mathematical models used to simulate the results of experimental observations. In many cases, there are input parameters to these models which are difficult to determine via direct measurement, and it is desirable to invert the numerical model -- that is, use the experimental observations to determine values of the input parameters. Bayesian inference is a fruitful framework within which to do such fitting, since the resulting posterior probability distribution over the parameters of interest can give rich insights into not just the most likely values of the parameters, but also uncertainty about these values and the potentially complicated ways in which they can covary to give equally good fits to observations.', br=True)
-
[…]

### 2019-05-30 setup.py

@@ -2,7 +2,7 @@ from setuptools import setup, find_packages
 import os
 
 setup(name='bayesim',
-      version='0.9.5',
+      version='0.9.7',
       description='Fast model fitting via Bayesian inference',
       author='Rachel Kurchin, Giuseppe Romano',
       author_email='rkurchin@mit.edu, romanog@mit.edu',
@@ -15,7 +15,8 @@ setup(name='bayesim',
                         'matplotlib',
                         'joblib'
                          ],
-      license='GPLv2',\
+      dependency_links=['https://github.com/slwatkins/deepdish/tarball/master#egg=deepdish-0.3.4'],
+      license='GPLv2',
       packages = ['bayesim'],
       entry_points = {
      'console_scripts': [

### 2019-05-30 setup.py
I think deepdish thing is fixed now

@@ -1,21 +1,60 @@
 from setuptools import setup, find_packages
-import os
+import os, sys
+
+"""The setup script."""
+
+try: # for pip >= 10
+    from pip._internal import req
+except ImportError: # for pip <= 9.0.3
+    from pip import req
+
+with open('README.rst') as readme_file:
+    readme = readme_file.read()
+
+history = ''
+
+links = []
+requires = []
+try:
+    requirements = list(req.parse_requirements(os.path.abspath('requirements.txt')))
+except TypeError:
+
+    try:
+        from pip import download
+    except ImportError:
+        from pip._internal import download
+    
+    # new versions of pip requires a session
+    requirements = req.parse_requirements(
+        os.path.abspath('requirements.txt'), session=download.PipSession())
+
+for item in requirements:
+    req = item.req
+    # we want to handle package names and also repo urls
+    if getattr(item, 'url', None):  # older pip has url
+        links.append(str(item.url))
+        if req:
+            req = "==".join(str(req).split("-", 1))
+    if getattr(item, 'link', None): # newer pip has link
+        links.append(str(item.link))
+        if req:
+            req = "==".join(str(req).split("-", 1))
+    if req:
+        requires.append(str(req))
+
+print(requires)
+print()
+print(links)
 
 setup(name='bayesim',
-      version='0.9.7',
+      version='0.9.14',
       description='Fast model fitting via Bayesian inference',
       author='Rachel Kurchin, Giuseppe Romano',
       author_email='rkurchin@mit.edu, romanog@mit.edu',
-      classifiers=['Programming Language :: Python :: 3.6'],
+      classifiers=['Programming Language :: Python :: 3.7'],
       long_description=open('README.rst').read(),
-      install_requires=['pandas',
-                        'deepdish',
-                        'numpy',
-                        'scipy',
-                        'matplotlib',
-                        'joblib'
-                         ],
-      dependency_links=['https://github.com/slwatkins/deepdish/tarball/master#egg=deepdish-0.3.4'],
+      install_requires=requires,
+      dependency_links=links,
       license='GPLv2',
       packages = ['bayesim'],
       entry_points = {

### 2019-05-30 setup.py
updating docs with new install instructions

@@ -47,7 +47,7 @@ print()
 print(links)
 
 setup(name='bayesim',
-      version='0.9.14',
+      version='0.9.15',
       description='Fast model fitting via Bayesian inference',
       author='Rachel Kurchin, Giuseppe Romano',
       author_email='rkurchin@mit.edu, romanog@mit.edu',

### 2019-05-30 bayesim/ddconf.py
fixed ideal_diode.ipynb

@@ -1,0 +1,20 @@
+from __future__ import division, print_function, absolute_import
+import os
+import sys
+if sys.version_info >= (3,):
+    from configparser import ConfigParser
+else:
+    from ConfigParser import ConfigParser
+
+
+def config():
+    """
+    Loads and returns a ConfigParser from ``~/.deepdish.conf``.
+    """
+    conf = ConfigParser()
+    # Set up defaults
+    conf.add_section('io')
+    conf.set('io', 'compression', 'zlib')
+
+    conf.read(os.path.expanduser('~/.deepdish.conf'))
+    return conf

### 2019-05-30 bayesim/hdf5io.py

@@ -1,0 +1,682 @@
+from __future__ import division, print_function, absolute_import
+
+import numpy as np
+import tables
+import warnings
+from scipy import sparse
+#from deepdish import conf
+import bayesim.ddconf as conf
+try:
+    import pandas as pd
+    pd.io.pytables._tables()
+    _pandas = True
+except ImportError:
+    _pandas = False
+
+try:
+    from types import SimpleNamespace
+    _sns = True
+except ImportError:
+    _sns = False
+
+#from deepdish import six
+import bayesim.six as six
+
+IO_VERSION = 12
+DEEPDISH_IO_PREFIX = 'DEEPDISH_IO'
+DEEPDISH_IO_VERSION_STR = DEEPDISH_IO_PREFIX + '_VERSION'
+DEEPDISH_IO_UNPACK = DEEPDISH_IO_PREFIX + '_DEEPDISH_IO_UNPACK'
+DEEPDISH_IO_ROOT_IS_SNS = DEEPDISH_IO_PREFIX + '_ROOT_IS_SNS'
+
+# Types that should be saved as pytables attribute
+ATTR_TYPES = (int, float, bool, six.string_types, six.binary_type,
+              np.int8, np.int16, np.int32, np.int64, np.uint8,
+              np.uint16, np.uint32, np.uint64, np.float16, np.float32,
+              np.float64, np.bool_, np.complex64, np.complex128)
+
+if _pandas:
+    class _HDFStoreWithHandle(pd.io.pytables.HDFStore):
+        def __init__(self, handle):
+            self._path = None
+            self._complevel = None
+            self._complib = None
+            self._fletcher32 = False
+            self._filters = None
+
+            self._handle = handle
+
+
+def is_pandas_dataframe(level):
+    return ('pandas_version' in level._v_attrs and
+            'pandas_type' in level._v_attrs)
+
+
+class ForcePickle(object):
+    """
+    When saving an object with `deepdish.io.save`, you can wrap objects in this
+    class to force them to be pickled. They will automatically be unpacked at
+    load time.
+    """
+    def __init__(self, obj):
+        self.obj = obj
+
+
+class Compression(object):
+    """
+    Class to enable explicit compression settings for individual arrays.
+    """
+    def __init__(self, obj, compression='default'):
+        self.obj = obj
+        self.compression = compression
+
+
+def _dict_native_ok(d):
+    """
+    This checks if a dictionary can be saved natively as HDF5 groups.
+
+    If it can't, it will be pickled.
+    """
[…]

### 2019-05-30 bayesim/model.py

@@ -1,8 +1,10 @@
+#import sys
+#sys.path.append('../')
 from bayesim.pmf import Pmf
 import bayesim.params as pm
 from bayesim.utils import calc_deltas, get_closest_val
 import pandas as pd
-import deepdish as dd
+import bayesim.hdf5io as dd
 from copy import deepcopy
 import numpy as np
 import matplotlib.pyplot as plt
@@ -45,7 +47,7 @@ class Model(object):
         if load_state:
             if verbose:
                 print('Loading bayesim state from %s...\n'%state_file)
-            state = dd.io.load(state_file)
+            state = dd.load(state_file)
 
             # variables
             self.ec_pts = state['ec_pts']
@@ -192,7 +194,7 @@ class Model(object):
         if verbose:
             print('Attaching measured data...\n')
 
-        self.obs_data = dd.io.load(argv['obs_data_path'])
+        self.obs_data = dd.load(argv['obs_data_path'])
         # get EC names if necessary
         cols = list(self.obs_data.columns)
         if output_col not in cols:
@@ -349,6 +351,7 @@ class Model(object):
         end_indices = np.zeros(len(self.probs.points),dtype=int)
         #print(list(self.model_data_grps.groups.keys())[:5])
         for pt in self.probs.points.iterrows():
+            #print(pt[1])
             #print(tuple(pt[1][self.fit_param_names()].tolist()))
             subset_inds = self.model_data_grps.groups[tuple(pt[1][self.fit_param_names()].tolist())]
             if len(subset_inds)==0:
@@ -382,7 +385,7 @@ class Model(object):
 
         if mode == 'file':
             # import and sort data on parameter values
-            self.model_data = dd.io.load(argv['model_data_path'])
+            self.model_data = dd.load(argv['model_data_path'])
 
             # Check that columns match EC's and parameter names
             # (and determine parameter names if need be)
@@ -396,15 +399,21 @@ class Model(object):
             param_points = pd.DataFrame.from_records(data=[list(k) for k in param_points_grps.groups.keys()],columns=self.fit_param_names()).sort_values(self.fit_param_names()).reset_index(drop=True)
 
             # if PMF has been populated, check that points match
+            # this check is broken ("Can only compare identically-labeled...")
+            # FIX ME
+            """
             if not self.probs.is_empty:
                 #print(len(param_points),len(self.probs.points[self.fit_param_names()]))
                 if not all(param_points==self.probs.points[self.fit_param_names()]):
[…]

### 2019-05-30 bayesim/params.py

@@ -1,5 +1,4 @@
 import numpy as np
-import deepdish as dd
 from decimal import *
 import json
 from copy import deepcopy

### 2019-05-30 setup.py

@@ -42,12 +42,8 @@ for item in requirements:
     if req:
         requires.append(str(req))
 
-print(requires)
-print()
-print(links)
-
 setup(name='bayesim',
-      version='0.9.15',
+      version='0.9.16',
       description='Fast model fitting via Bayesian inference',
       author='Rachel Kurchin, Giuseppe Romano',
       author_email='rkurchin@mit.edu, romanog@mit.edu',

### 2019-05-30 docs/conf.py
hopefully this fixes the Binder

@@ -28,7 +28,7 @@ author = 'Rachel C Kurchin and Giuseppe Romano'
 # The short X.Y version
 version = ''
 # The full version, including alpha/beta/rc tags
-release = '0.9.5'
+release = '0.9.16'
 
 
 # -- General configuration ---------------------------------------------------

### 2019-05-30 setup.py

@@ -1,47 +1,6 @@
 from setuptools import setup, find_packages
 import os, sys
 
-"""The setup script."""
-
-try: # for pip >= 10
-    from pip._internal import req
-except ImportError: # for pip <= 9.0.3
-    from pip import req
-
-with open('README.rst') as readme_file:
-    readme = readme_file.read()
-
-history = ''
-
-links = []
-requires = []
-try:
-    requirements = list(req.parse_requirements(os.path.abspath('requirements.txt')))
-except TypeError:
-
-    try:
-        from pip import download
-    except ImportError:
-        from pip._internal import download
-    
-    # new versions of pip requires a session
-    requirements = req.parse_requirements(
-        os.path.abspath('requirements.txt'), session=download.PipSession())
-
-for item in requirements:
-    req = item.req
-    # we want to handle package names and also repo urls
-    if getattr(item, 'url', None):  # older pip has url
-        links.append(str(item.url))
-        if req:
-            req = "==".join(str(req).split("-", 1))
-    if getattr(item, 'link', None): # newer pip has link
-        links.append(str(item.link))
-        if req:
-            req = "==".join(str(req).split("-", 1))
-    if req:
-        requires.append(str(req))
-
 setup(name='bayesim',
       version='0.9.16',
       description='Fast model fitting via Bayesian inference',
@@ -49,8 +8,7 @@ setup(name='bayesim',
       author_email='rkurchin@mit.edu, romanog@mit.edu',
       classifiers=['Programming Language :: Python :: 3.7'],
       long_description=open('README.rst').read(),
-      install_requires=requires,
-      dependency_links=links,
+      install_requires=['pandas', 'scipy', 'matplotlib', 'joblib', 'tables']
       license='GPLv2',
       packages = ['bayesim'],
       entry_points = {

### 2019-05-30 setup.py
typo

@@ -8,7 +8,7 @@ setup(name='bayesim',
       author_email='rkurchin@mit.edu, romanog@mit.edu',
       classifiers=['Programming Language :: Python :: 3.7'],
       long_description=open('README.rst').read(),
-      install_requires=['pandas', 'scipy', 'matplotlib', 'joblib', 'tables']
+      install_requires=['pandas', 'scipy', 'matplotlib', 'joblib', 'tables'],
       license='GPLv2',
       packages = ['bayesim'],
       entry_points = {
